---
title: "03.Application_plots.Rmd"
author: "Cora Burgwinkel"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "..")   # paths relative to the repository root, as in 01 and 02

# load libaries
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(MASS)
library(Matrix)
library(metafor)
```

# Plot Univariate for seizure reduction

```{r, fig.width = 10, fig.height = 10}
final_uni_df_O1 <- read.csv2("Data/data_uni_df_O1.csv", sep = ",")

final_uni_df_O1 <- final_uni_df_O1 %>%
  mutate(across(c(Selection, Estimate_adjusted, Estimate_unadjusted,
                   CI_adjusted_lower, CI_adjusted_upper, Estimate_unadjusted,
                  CI_unadjusted_lower, CI_unadjusted_upper), as.numeric))

# plot the different z-scores for unadjusted and adjusted estimates
ggplot(data = final_uni_df_O1, aes(x = as.numeric(Selection))) +
  # Add ribbons for confidence intervals
  geom_ribbon(aes(ymin = CI_adjusted_lower, ymax = CI_adjusted_upper, fill = "Adjusted CI"), alpha = 0.2) +
  geom_ribbon(aes(ymin = CI_unadjusted_lower, ymax = CI_unadjusted_upper, fill = "Unadjusted CI"), alpha = 0.1) +
  # Add adjusted estimate line and point
  geom_line(aes(y = Estimate_adjusted, color = "Adjusted Estimate"), linewidth = 1) +
  geom_point(aes(y = Estimate_adjusted, color = "Adjusted Estimate"), size = 2) +
  # Add unadjusted estimate line
  geom_line(aes(y = Estimate_unadjusted, color = "Naive Estimate"),
            linetype = "dashed", linewidth = 1) +
  # Facet by z_score and effect_estimate
  facet_grid(Z_score ~ Measure,
             labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                                     "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                 Z_score = c("TRUE" = "Selection on Z-score",
                                             "FALSE" = "Selection on log OR/log RR"))) +
  # Define scales for colors and fill
  scale_color_manual(name = " ",
                     values = c("Adjusted Estimate" = "blue", "Naive Estimate" = "red")) +
  scale_fill_manual(name = "Confidence Interval",
                    values = c("Adjusted CI" = "blue", "Unadjusted CI" = "red"),
                    guide = "none") +
  # Add labels and theme adjustments
  labs(x = expression("Selection Weight"~delta), y = "Overall Summary Estimate") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.text = element_text(size = 16))

ggsave("Plots_Paper/App_Uni_REM_O1.png", width = 10, height = 10)
```


# Plot Univariate for seizure freedom

```{r, fig.width = 10, fig.height = 10}
final_uni_df_O2 <- read.csv2("Data/data_uni_df_O2.csv", sep = ",")

final_uni_df_O2 <- final_uni_df_O2 %>%
  mutate(across(c(Estimate_adjusted, Estimate_unadjusted,
                   CI_adjusted_lower, CI_adjusted_upper, Estimate_unadjusted,
                  CI_unadjusted_lower, CI_unadjusted_upper), as.numeric))

# plot the different z-scores for unadjusted and adjusted estimates
ggplot(data = final_uni_df_O2, aes(x = as.numeric(Selection))) +
  # Add ribbons for confidence intervals
  geom_ribbon(aes(ymin = CI_adjusted_lower, ymax = CI_adjusted_upper, fill = "Adjusted CI"), alpha = 0.2) +
  geom_ribbon(aes(ymin = CI_unadjusted_lower, ymax = CI_unadjusted_upper, fill = "Unadjusted CI"), alpha = 0.1) +
  # Add adjusted estimate line and point
  geom_line(aes(y = Estimate_adjusted, color = "Adjusted Estimate"), linewidth = 1) +
  geom_point(aes(y = Estimate_adjusted, color = "Adjusted Estimate"), size = 2) +
  # Add unadjusted estimate line
  geom_line(aes(y = Estimate_unadjusted, color = "Naive Estimate"),
            linetype = "dashed", linewidth = 1) +
  # Facet by z_score and effect_estimate
  facet_grid(Z_score ~ Measure,
             labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                                     "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                 Z_score = c("TRUE" = "Selection on Z-score",
                                             "FALSE" = "Selection on log OR/log RR"))) +
  # Define scales for colors and fill
  scale_color_manual(name = " ",
                     values = c("Adjusted Estimate" = "blue", "Naive Estimate" = "red")) +
  scale_fill_manual(name = "Confidence Interval",
                    values = c("Adjusted CI" = "blue", "Unadjusted CI" = "red"),
                    guide = "none") +
  # Add labels and theme adjustments
  labs(x = expression("Selection Weight"~delta), y = "Overall Summary Estimate") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.text = element_text(size = 16))

ggsave("Plots_Paper/App_Uni_REM_O2.png", width = 10, height = 10)
```


# Plot Comparison of Correlations
## for 50% Seizure Reduction

```{r, fig.width = 10, fig.height = 10}

plot_biv_df <- read.csv2("Data/data_biv_df.csv", sep = ",")

# only plot outcome one
plot_biv_df_O1 <- subset(plot_biv_df, Outcome == "O1")

# bring data into wide format
naive_df_O1 <- plot_biv_df_O1 %>%
 filter(Approach == "Naive estimate") %>%
 dplyr::select(Outcome, Measure, Selection, Correlation,
        Estimate_unadjusted = Estimate,
        CI_unadjusted_lower = CI_Lower,
        CI_unadjusted_upper = CI_Upper)
 
adjusted_df_O1 <- plot_biv_df_O1 %>%
 filter(Approach != "Naive estimate") %>%
 # Create the Z_score column your plot expects (TRUE if zscore, FALSE if effect)
 mutate(Z_score = ifelse(Approach == "Bivariate Selection on zscore", TRUE, FALSE)) %>%
 dplyr::select(Outcome, Measure, Selection, Z_score, Correlation,
        Estimate_adjusted = Estimate, 
        CI_adjusted_lower = CI_Lower, 
        CI_adjusted_upper = CI_Upper)
 
final_biv_df_O1 <- adjusted_df_O1 %>%
 left_join(naive_df_O1, by = c("Selection", "Measure", "Correlation", "Outcome")) 

# plot all correlations together
 
# rename correlations
final_biv_df_O1$Correlation[final_biv_df_O1$Correlation == "studyspecific"] <- "Study-specific"
final_biv_df_O1$Correlation[final_biv_df_O1$Correlation == "estimated"] <- "Global"

# factor correlation such that it is depicted in the correct order in the legend
final_biv_df_O1$Correlation <- factor(
  final_biv_df_O1$Correlation, 
  levels = c("-0.9", "-0.6", "-0.3", "0", "0.3", "0.6", "0.67", "Global", "Study-specific"))

# plot correlation over different colors
ggplot(data = final_biv_df_O1, aes(x = as.numeric(Selection))) +
   # Adjusted estimates: color by Correlation
  geom_line(aes(y = as.numeric(Estimate_adjusted), color = Correlation),
           linewidth = 1, linetype = "solid") +
  geom_point(aes(y = as.numeric(Estimate_adjusted), color = Correlation,
            shape = Correlation), size = 2) +
    # Facets
   facet_grid(Z_score ~ Measure,
              labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                              "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                  Z_score = c("TRUE" = "Selection on Z-score",
                                              "FALSE" = "Selection on log OR/log RR"))) +
     # Manual scales
    scale_color_manual(name = "Correlation",
                      values = c("-0.9" = "lightblue", "-0.6" = "#92C5DE",
                                 "-0.3" = "#4393C3", "0" = "cornflowerblue",
                                 "0.3" = "#2166AC", "0.6" = "skyblue4", "0.67" = "#03045E",
                                 "Study-specific" = "red", "Global" = "forestgreen")) +
    scale_shape_manual(name = "Correlation",
                      values = c("-0.9" = 16, "-0.6" = 17, "-0.3" = 18,
                                 "0" = 19, "0.3" = 20, "0.6" = 0, "0.67" = 5,
                                 "Study-specific" = 21, "Global" = 22)) +
    # Labels and theme
    labs(x = expression("Selection Weight"~delta), y = "Overall Summary Measure") +
    theme_minimal() +
    theme(legend.position = "bottom",
         panel.spacing.x = unit(1, "cm"),
         panel.spacing.y = unit(1, "lines"),
         axis.title.x = element_text(size = 16),
         axis.title.y = element_text(size = 16),
         legend.text = element_text(size = 16),
         legend.title = element_text(size = 16),
         strip.text = element_text(size = 16)) 

ggsave("Plots_Paper/App_Corr_12_mv_REM_O1.png", width = 10, height = 10)

```

## for Seizure Freedom

```{r, fig.width = 10, fig.height = 10}

# only plot outcome two
plot_biv_df_O2 <- subset(plot_biv_df, Outcome == "O2")

# bring data into wide format
naive_df <- plot_biv_df_O2 %>%
 filter(Approach == "Naive estimate") %>%
 dplyr::select(Outcome, Measure, Selection, Correlation,
        Estimate_unadjusted = Estimate,
        CI_unadjusted_lower = CI_Lower,
        CI_unadjusted_upper = CI_Upper)
 
adjusted_df <- plot_biv_df_O2 %>%
 filter(Approach != "Naive estimate") %>%
 # Create the Z_score column your plot expects (TRUE if zscore, FALSE if effect)
 mutate(Z_score = ifelse(Approach == "Bivariate Selection on zscore", TRUE, FALSE)) %>%
 dplyr::select(Outcome, Measure, Selection, Z_score, Correlation,
        Estimate_adjusted = Estimate, 
        CI_adjusted_lower = CI_Lower, 
        CI_adjusted_upper = CI_Upper)
 
final_biv_df <- adjusted_df %>%
 left_join(naive_df, by = c("Selection", "Measure", "Correlation", "Outcome")) 

# plot all correlations together
 
# rename correlations
final_biv_df$Correlation[final_biv_df$Correlation == "studyspecific"] <- "Study-specific"
final_biv_df$Correlation[final_biv_df$Correlation == "estimated"] <- "Global"

# factor correlation such that it is depicted in the correct order in the legend
final_biv_df$Correlation <- factor(
  final_biv_df$Correlation, 
  levels = c("-0.9", "-0.6", "-0.3", "0", "0.3", "0.6", "0.67", "Global", "Study-specific"))


# plot correlation over different colors
ggplot(data = final_biv_df, aes(x = as.numeric(Selection))) +
   # Adjusted estimates: color by Correlation
  geom_line(aes(y = as.numeric(Estimate_adjusted), color = Correlation),
           linewidth = 1, linetype = "solid") +
  geom_point(aes(y = as.numeric(Estimate_adjusted), color = Correlation,
            shape = Correlation), size = 2) +
    # Facets
   facet_grid(Z_score ~ Measure,
              labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                              "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                  Z_score = c("TRUE" = "Selection on Z-score",
                                              "FALSE" = "Selection on log OR/log RR"))) +
     # Manual scales
     scale_color_manual(name = "Correlation",
                      values = c("-0.9" = "lightblue", "-0.6" = "#92C5DE",
                                 "-0.3" = "#4393C3", "0" = "cornflowerblue",
                                 "0.3" = "#2166AC", "0.6" = "skyblue4", "0.67" = "#03045E",
                                 "Study-specific" = "red", "Global" = "forestgreen")) +
     scale_shape_manual(name = "Correlation",
                      values = c("-0.9" = 16, "-0.6" = 17, "-0.3" = 18,
                                 "0" = 19, "0.3" = 20, "0.6" = 0, "0.67" = 5,
                                 "Study-specific" = 21, "Global" = 22)) +
    # Labels and theme
    labs(x = expression("Selection Weight"~delta), y = "Overall Summary Measure") +
    theme_minimal() +
    theme(legend.position = "bottom",
         panel.spacing.x = unit(1, "cm"),
         panel.spacing.y = unit(1, "lines"),
         axis.title.x = element_text(size = 16),
         axis.title.y = element_text(size = 16),
         legend.text = element_text(size = 16),
         legend.title = element_text(size = 16),
         strip.text = element_text(size = 16))

ggsave("Plots_Paper/App_Corr_12_mv_REM_O2.png", width = 10, height = 10)
```

# Plot Univariate and Multivariate for comparison for seizure reduction
## within-study correlation of -0.3

```{r, fig.width = 10, fig.height = 10}

#data set for univariate
uni <- final_uni_df_O1 %>%
  dplyr::select(Z_score, Selection, Measure,
                Estimate_adjusted_uni = Estimate_adjusted,
                Estimate_unadjusted_uni = Estimate_unadjusted,
                CI_adjusted_low_uni = CI_adjusted_lower,
                CI_adjusted_up_uni = CI_adjusted_upper)

uni$Selection <- as.numeric(uni$Selection)
final_biv_df_O1$Selection <- as.numeric(final_biv_df_O1$Selection)

# select correlation
final_biv_df_O1 <- subset(final_biv_df_O1, Correlation == -0.3)

# merge with bivariate data
plotdf <- final_biv_df_O1 %>%
  dplyr::select(Z_score, Selection, Measure,
                Estimate_adjusted, Estimate_unadjusted,
                CI_adjusted_lower, CI_adjusted_upper) %>%
  left_join(uni, by = c("Measure", "Z_score","Selection"))

# make sure estimates are numerical
plotdf <- plotdf %>%
  mutate(across(c(Estimate_adjusted, Estimate_unadjusted,
                   CI_adjusted_lower, CI_adjusted_upper,
                  Estimate_adjusted_uni, Estimate_unadjusted_uni,
                  CI_adjusted_low_uni, CI_adjusted_up_uni), as.numeric))


# Create the ggplot
ggplot(data = plotdf, aes(x = as.numeric(Selection))) +
  # Add ribbons for confidence intervals
  geom_ribbon(aes(ymin = as.numeric(CI_adjusted_low_uni), ymax = as.numeric(CI_adjusted_up_uni), fill = "Adjusted CI Univariate"), alpha = 0.2) +
  geom_ribbon(aes(ymin = CI_adjusted_lower, ymax = CI_adjusted_upper, fill = "Adjusted CI Bivariate"), alpha = 0.1) +
  # Add adjusted estimate line and point
  geom_line(aes(y = as.numeric(Estimate_adjusted), color = "Adjusted - Bivariate"), linewidth = 1) +
  geom_line(aes(y = as.numeric(Estimate_adjusted_uni), color = "Adjusted - Univariate"), linewidth = 1) +
  geom_point(aes(y = as.numeric(Estimate_adjusted), color = "Adjusted - Bivariate"), size = 2) +
  geom_point(aes(y = as.numeric(Estimate_adjusted_uni), color = "Adjusted - Univariate"), size = 2) +
  # Add unadjusted estimate line
  geom_line(aes(y = as.numeric(Estimate_unadjusted), color = "Naive - Bivariate"), linetype = "dashed", linewidth = 1) +
  geom_line(aes(y = as.numeric(Estimate_unadjusted_uni), color = "Naive - Univariate"), linetype = "dashed", linewidth = 1) +
  # Facet by z_score and effect_estimate
  facet_grid(Z_score ~ Measure,
             labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                             "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                 Z_score = c("TRUE" = "Selection on Z-score",
                                             "FALSE" = "Selection on log OR/log RR"))) +
  # Define scales for colors and fill
  scale_color_manual(name = " ",
                     values = c("Adjusted - Univariate" = "blue",
                                "Adjusted - Bivariate" = "#009E73",
                                "Naive - Bivariate" = "#009E73",
                                "Naive - Univariate" = "blue")) +
  scale_fill_manual(name = "Confidence Interval",
                    values = c("Adjusted CI Univariate" = "blue",
                               "Adjusted CI Bivariate" = "#009E73"),
                    guide = "none") +
  # Add labels and theme adjustments
  labs(x = expression("Selection Weight"~delta), y = "Overall Summary Measure") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.spacing.x = unit(1, "cm"),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.text = element_text(size = 16))

ggsave("Plots_Paper/Uni_Multi_Comp_12_REM_01.png", width = 10, height = 10)
```


# Plot Univariate and Multivariate for comparison for seizure freedom
## within-study correlation of -0.3

```{r, fig.width = 10, fig.height = 10}

#data set for univariate
uni <- final_uni_df_O2 %>%
  dplyr::select(Z_score, Selection, Measure,
                Estimate_adjusted_uni = Estimate_adjusted,
                Estimate_unadjusted_uni = Estimate_unadjusted,
                CI_adjusted_low_uni = CI_adjusted_lower,
                CI_adjusted_up_uni = CI_adjusted_upper)

uni$Selection <- as.numeric(uni$Selection)
final_biv_df$Selection <- as.numeric(final_biv_df$Selection)

# select correlation
final_biv_df1 <- subset(final_biv_df, Correlation == -0.3)

# merge with bivariate data
plotdf <- final_biv_df1 %>%
  dplyr::select(Z_score, Selection, Measure,
                Estimate_adjusted, Estimate_unadjusted,
                CI_adjusted_lower, CI_adjusted_upper) %>%
  left_join(uni, by = c("Measure", "Z_score","Selection"))

# make sure estimates are numerical
plotdf <- plotdf %>%
  mutate(across(c(Estimate_adjusted, Estimate_unadjusted,
                   CI_adjusted_lower, CI_adjusted_upper,
                  Estimate_adjusted_uni, Estimate_unadjusted_uni,
                  CI_adjusted_low_uni, CI_adjusted_up_uni), as.numeric))


# Create the ggplot
ggplot(data = plotdf, aes(x = as.numeric(Selection))) +
  # Add ribbons for confidence intervals
  geom_ribbon(aes(ymin = as.numeric(CI_adjusted_low_uni), ymax = as.numeric(CI_adjusted_up_uni), fill = "Adjusted CI Univariate"), alpha = 0.2) +
  geom_ribbon(aes(ymin = CI_adjusted_lower, ymax = CI_adjusted_upper, fill = "Adjusted CI Bivariate"), alpha = 0.1) +
  # Add adjusted estimate line and point
  geom_line(aes(y = as.numeric(Estimate_adjusted), color = "Adjusted - Bivariate"), linewidth = 1) +
  geom_line(aes(y = as.numeric(Estimate_adjusted_uni), color = "Adjusted - Univariate"), linewidth = 1) +
  geom_point(aes(y = as.numeric(Estimate_adjusted), color = "Adjusted - Bivariate"), size = 2) +
  geom_point(aes(y = as.numeric(Estimate_adjusted_uni), color = "Adjusted - Univariate"), size = 2) +
  # Add unadjusted estimate line
  geom_line(aes(y = as.numeric(Estimate_unadjusted), color = "Naive - Bivariate"), linetype = "dashed", linewidth = 1) +
  geom_line(aes(y = as.numeric(Estimate_unadjusted_uni), color = "Naive - Univariate"), linetype = "dashed", linewidth = 1) +
  # Facet by z_score and effect_estimate
  facet_grid(Z_score ~ Measure,
             labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                             "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                 Z_score = c("TRUE" = "Selection on Z-score",
                                             "FALSE" = "Selection on log OR/log RR"))) +
  # Define scales for colors and fill
  scale_color_manual(name = " ",
                     values = c("Adjusted - Univariate" = "blue",
                                "Adjusted - Bivariate" = "#009E73",
                                "Naive - Bivariate" = "#009E73",
                                "Naive - Univariate" = "blue")) +
  scale_fill_manual(name = "Confidence Interval",
                    values = c("Adjusted CI Univariate" = "blue",
                               "Adjusted CI Bivariate" = "#009E73"),
                    guide = "none") +
  # Add labels and theme adjustments
  labs(x = expression("Selection Weight"~delta), y = "Overall Summary Measure") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.spacing.x = unit(1, "cm"),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.text = element_text(size = 16))

ggsave("Plots_Paper/Uni_Multi_Comp_12_REM.png", width = 10, height = 10)
```

# Create forest plot for comparison of our approaches

```{r, warning = FALSE}
# read data in from Table_2.rds
data <- readRDS("Data/Table_2.rds")

# transform data to plot them as forest plot
dat <- data %>%
  # Standardize Approach names 
  mutate(
    Approach = case_when(
      Approach == "Selection on effect" ~ "Selection on effect estimate",
      Approach == "Selection on zscore" ~ "Selection on z-score",
      Approach == "Bivariate Selection on effect" ~ "Selection on effect estimate",
      Approach == "Bivariate Selection on zscore" ~ "Selection on z-score",
      TRUE ~ Approach
    ),
    #  Re-format the Model column
    Model = if_else(Correlation == "Univariate", "Univariate", paste0("Bivariate (", Correlation, ")")),
    # Clean up the Measure column
    Effect = str_remove(Measure, "log ")
  ) %>%
  # Pivot the two outcomes into a long format
  pivot_longer(
    cols = starts_with("Outcome"),
    names_to = c("Outcome", ".value"),
    names_pattern = "Outcome (\\d+)_(.*)"
  ) %>%
  #  Rename outcome numbers to your descriptive labels
  mutate(
    Outcome = if_else(Outcome == "1", "50% Seizure Reduction", "Seizure Freedom")
  ) %>%
  mutate(est = str_remove(Est_SE, " \\(.*\\)"
                          )) %>%
  #  Separate the confidence intervals into low (lcl) and high (ucl) bounds
  separate_wider_delim(
    cols = CI_95, 
    delim = " to ", 
    names = c("lcl", "ucl")
  ) %>%
  # Clean up data types 
  mutate(
    lcl = as.numeric(lcl),
    ucl = as.numeric(ucl),
    est = as.numeric(est)
  ) %>%
  #select/reorder the final columns
  dplyr::select(Model, Effect, Approach, Outcome, est, lcl, ucl)
```


```{r, warning = FALSE}
# Ordering
dat <- dat %>%
  mutate(
    Model = factor(
      Model,
      levels = c("Univariate",
                 "Bivariate (r = 0)",
                 "Bivariate (r = 0.7)")),
    Approach = factor(
      Approach,
      levels = c("Naive estimate",
                 "Selection on effect estimate",
                 "Selection on z-score"))) %>%
  arrange(Model, Approach)

# create the label for ploting
dat$Label <- factor(
  dat$Approach,
  levels = rev(c("Naive estimate",
                 "Selection on effect estimate",
                 "Selection on z-score")))

dat$Label <- factor(dat$Label,
                   levels = rev(unique(dat$Label)))
```

```{r, warning = FALSE, fig.width=10, fig.height=6}

# have enough space between imputation models, otherwise they are plotted on
# top of each other
pd <- position_dodge(width = 0.6, 
                     reverse = TRUE)

ggplot(dat,
       aes(x = est, y = Label, xmin = lcl, xmax = ucl, colour = Model)) +
  geom_vline(xintercept = 0, linetype = 2, colour = "grey40") +
  geom_errorbarh(width = 0.15, linewidth = 0.7, position = pd) +
  geom_point(size = 3, position = pd) +
  facet_grid(Effect ~ Outcome, 
             scales = "free_y", space = "free_y") +
  # label the bivariate models by the within-study correlation (rho_B is estimated)
  scale_colour_discrete(labels = c("Univariate",
                                   expression("Bivariate ("*rho[W]*" = 0)"),
                                   expression("Bivariate ("*rho[W]*" = 0.7)"))) +
  labs(x = "Log (OR)/ Log (RR)",
       y = NULL,
       colour = "Imputation model") +
  theme_bw(base_size = 16) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.background = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        strip.text = element_text(face = "bold"),
        axis.text.y = element_text(size = 16, colour = "black"))


ggsave("Plots_Paper/Forestplot.png", width = 10, height = 6)
```

# Create forest plot for comparison to existing methods
### for seizure freedom

```{r}
# read data in
data_topiramate <- data.frame(
  Study_id = 1:12,
  Author = c("Ben-Menachem", "Elterman", "Faught", "Guberman", "Korean", 
             "Privitera", "Rosenfeld", "Sharief", "Tassinari", "Yen", 
             "Zhang", "Coles"),
  
  # Sample Sizes (T = Treated, C = Control)
  N_t = c(28, 41, 136, 171, 91, 143, 167, 23, 30, 23, 46, 52),
  N_c = c(28, 45, 45, 92, 86,  47, 42, 24, 30, 23, 40, 51),
  
  # Outcome 1: 50% Seizure Reduction
  T1 = c(12, 16, 54, 77, 45, 58, 86, 8, 14, 11, 22, NA),
  C1 = c(0, 9, 8, 22, 11, 4, 8, 2, 3, 3, 3, NA),
  
  # Outcome 2: Seizure Freedom
  T2 = c (NA, 4, NA, 10, 7, NA, NA, 2, 0, NA, 0, NA),
  C2 = c (NA, 2, NA,  2, 1, NA, NA, 0, 0, NA, 0, NA)
)



# ORBIT classification
orbit_to_risk <- c(A = "HR", D = "HR", E = "HR", G = "HR",   # High Risk
                   C = "LR", F = "LR", H = "LR",             # Low Risk
                   B = "NR", I = "NR")                       # No Risk

# Seizure Reduction (outcome 1) — from Table 3 Copas et al. 2019
orbit_code_outcome1 <- c(
  "Coles"        = "E"
  # remaining studies fully report seizure reduction -> not in this vector
)

# Seizure freedom (outcome 2) — from Table 3 Copas et al. 2019
orbit_code_outcome2 <- c(
  "Ben-Menachem" = "E",
  "Faught"       = "E",
  "Privitera"    = "E",
  "Rosenfeld"    = "C",
  "Yen"          = "E",
   "Coles"  = "E"
  # remaining studies fully report seizure freedom -> not in this vector
)

data_topiramate$orbit_out1 <- orbit_to_risk[orbit_code_outcome1[data_topiramate$Author]]
data_topiramate$orbit_out2 <- orbit_to_risk[orbit_code_outcome2[data_topiramate$Author]]

```

```{r}
compute_effects <- function(data) {
   # --------------------------------------
  # OUTCOME 1: Seizure Reduction
  # --------------------------------------
  
   # Log Relative Risk
  data <- escalc(measure = "RR", 
                 ai = T1, 
                 n1i = N_t, 
                 ci = C1, 
                 n2i = N_c, 
                 data = data, 
                 var.names = c("log_RR1", "var_RR1"), 
                 append = TRUE,
                 add = 0.5, 
                 to = "only0")
  # Convert variance to SE
  data$se_RR1 <- sqrt(data$var_RR1)
  
  # --------------------------------------
  # OUTCOME 2: Seizure Freedom
  # --------------------------------------
  
  # Log Relative Risk
  data <- escalc(measure = "RR", 
                 ai = T2, 
                 n1i = N_t, 
                 ci = C2, 
                 n2i = N_c, 
                 data = data, 
                 var.names = c("log_RR2", "var_RR2"),
                 append = TRUE,
                 add = 0.5, 
                 to = "only0")
  # Convert variance to SE
  data$se_RR2 <- sqrt(data$var_RR2)
  
  data_out <- data |> 
    dplyr::mutate(n_total = N_t + N_c) |> 
    dplyr::select(Study_id,
                  orbit_out1,
                  orbit_out2,
                  n_total, 
                  log_RR1, 
                  se_RR1,
                  log_RR2, 
                  se_RR2)  
  
  return(data_out)
}

data_topiramate <- compute_effects(data_topiramate)

# slightly different function than the one in 00.functions.R
impute_missing_se <- function(data, 
                              target_theta_col, 
                              target_se_col) {
  
  # Identify reported and unreported indices
  rep_idx <- which(!is.na(data[[target_theta_col]]))
  unrep_idx <- which(is.na(data[[target_theta_col]]))
  
  # If there are no missing values for this outcome, return data 
  if(length(unrep_idx) == 0) {
    return(data)
  }
  
  # Calculate k_hat using only the reported studies (Eq. 6)
  # Precision is the inverse of the variance (1 / SE^2)
  precisions <- 1 / (data[[target_se_col]][rep_idx]^2)
  k_hat <- sum(precisions) / sum(data$n_total[rep_idx])
  
  # Impute the missing standard errors
  data[[target_se_col]][unrep_idx] <- sqrt(1 / (k_hat * data$n_total[unrep_idx]))
  
  return(data)
}

data_topiramate <- impute_missing_se(
  data = data_topiramate, 
  target_theta_col = "log_RR1", 
  target_se_col = "se_RR1"
)

data_topiramate <- impute_missing_se(
  data = data_topiramate, 
  target_theta_col = "log_RR2", 
  target_se_col = "se_RR2"
)
```

```{r}
# -------------------------------------------------------------------
# Copas ORB Selection Model for Benefit Outcomes (Copas et al.)
# -------------------------------------------------------------------
copas_orb_adjustment <- function(data, 
                                 theta_col = "log_RR2", 
                                 se_col    = "se_RR2", 
                                 risk_col  = "orbit_out2", 
                                 alpha     = 0.05) {
  
  z_alpha <- qnorm(1 - alpha / 2)
  
  reported <- data[!is.na(data[[theta_col]]), ]
  w_rep    <- 1 / (reported[[se_col]]^2)
  theta_U  <- sum(w_rep * reported[[theta_col]]) / sum(w_rep)
  se_theta <- sqrt(1 / sum(w_rep))
  
  hr_studies <- data[is.na(data[[theta_col]]) & (!is.na(data[[risk_col]]) & data[[risk_col]] == "HR"), ]
  sigma_hr   <- hr_studies[[se_col]]
  
  if (length(sigma_hr) == 0) {
    return(data.frame(
      estimate_logRR = theta_U,
      ci_lower_logRR = theta_U - z_alpha * se_theta,
      ci_upper_logRR = theta_U + z_alpha * se_theta,
      estimate_RR    = exp(theta_U),
      ci_lower_RR    = exp(theta_U - z_alpha * se_theta),
      ci_upper_RR    = exp(theta_U + z_alpha * se_theta),
      p_value        = 2 * (1 - pnorm(abs(theta_U / se_theta)))
    ))
  }
  
  log_lik_B <- function(theta) {
    unadj_term <- - ((theta - theta_U)^2) / (2 * se_theta^2)
    p_non_sig  <- pnorm(z_alpha - theta / sigma_hr) - pnorm(-z_alpha - theta / sigma_hr)
    p_non_sig  <- pmax(p_non_sig, 1e-15)
    unadj_term + sum(log(p_non_sig))
  }
  
  opt     <- optimize(log_lik_B, interval = c(-10, 10), maximum = TRUE)
  theta_B <- opt$maximum
  max_ll  <- opt$objective
  
  lr_target <- function(theta) 2 * (max_ll - log_lik_B(theta)) - z_alpha^2
  
  ci_lower <- tryCatch({
    uniroot(lr_target, interval = c(-10, theta_B))$root
  }, error = function(e) theta_B - z_alpha * se_theta)
  
  ci_upper <- tryCatch({
    uniroot(lr_target, interval = c(theta_B, 10))$root
  }, error = function(e) theta_B + z_alpha * se_theta)
  
  p_val <- 1 - pchisq(pmax(0, 2 * (max_ll - log_lik_B(0))), df = 1)
  
  return(data.frame(
    estimate_logRR = theta_B,
    ci_lower_logRR = ci_lower,
    ci_upper_logRR = ci_upper,
    estimate_RR    = exp(theta_B),
    ci_lower_RR    = exp(ci_lower),
    ci_upper_RR    = exp(ci_upper),
    p_value        = p_val
  ))
}

copas_result <- copas_orb_adjustment(data_topiramate)
```




```{r}
# read data in, "unrep" for unreported studies
data_topiramate_unrep <- data.frame(
  Study_id = 1:12,
  Author = c("Ben-Menachem", "Elterman", "Faught", "Guberman", "Korean", 
             "Privitera", "Rosenfeld", "Sharief", "Tassinari", "Yen", 
             "Zhang", "Coles"),
  
  # Sample Sizes (T = Treated, C = Control)
  N_t = c(28, 41, 136, 171, 91, 143, 167, 23, 30, 23, 46, 52),
  N_c = c(28, 45, 45, 92, 86,  47, 42, 24, 30, 23, 40, 51),
  
  # Outcome 1: 50% Seizure Reduction
  T1 = c(12, 16, 54, 77, 45, 58, 86, 8, 14, 11, 22, "unrep"),
  C1 = c(0, 9, 8, 22, 11, 4, 8, 2, 3, 3, 3, "unrep"),
  
  # Outcome 2: Seizure Freedom
  T2 = c ("unrep", 4, "unrep", 10, 7, "unrep", "unrep", 2, 0, "unrep", 0, "unrep"),
  C2 = c ("unrep", 2, "unrep",  2, 1, "unrep", "unrep", 0, 0, "unrep", 0, "unrep")
)


# function from github
#The function reORBadj adjusts for ORB according to the selection model framework developed in this project
#It can be seen as an extension of the Copas et al. (2019) methodology, for the random effects model, and without
#the need for an ORBIT classification of unreported study outcomes.

#Inputs
#a - vector for observed counts in the treatment arm for each study in the meta-analysis, unreported study outcomes have entry "unrep"
#c - vector for observed counts in the control arm for each study in the meta-analysis, unreported study outcomes have entry "unrep"
#mu1 - vector for observed means in the treatment arm for each study in the meta-analysis, unreported study outcomes have entry "unrep"
#mu2 - vector for observed means in the control arm for each study in the meta-analysis, unreported study outcomes have entry "unrep"
#sd1 - vector for observed standard errors in the treatment arm for each study in the meta-analysis, unreported study outcomes have entry "unrep"
#sd2 - vector for observed standard errors in the control arm for each study in the meta-analysis, unreported study outcomes have entry "unrep"
#y - vector for observed treatment effects (normally distributed, eg log RR) for each study in the meta-analysis, unreported study outcomes have entry "unrep"
#s - vector for observed standard errors of the the treatment effect for each study in the meta-analysis, unreported study outcomes have entry "unrep"
#n1 - vector for sample sizes in treatment arm, must be reported for all studies
#n2 - vector for sample sizes in control arm, must be reported for all studies
#outcome - string character "beneficial"
#init_param - vector of length two, containing the values to be used for initialization of the joint optimization of the treatment effect and heterogeneity variance
#alpha_ben - value for desired confidence level, e.g., 0.05
#alpha_ben_one.sided - if TRUE, one sided significance is used, FALSE for two-sided
#true.SE - if the true standard errors are known, valid only for the case in which we have y and s as inputs; in this case the SE are not imputed
#LR.CI - if TRUE, calculates the profile likelihood confidence intervals using the likelihood ratio statistic
#Wald.CI - if TRUE, calculates Wald CI 
#selection.benefit - string factor specifying the selection function to be used for the ORB adjustment 
#                  "Constant-constant" W_A in manuscript
#                  "Constant-continous" W_B in manuscript
#                  "Continous-constant" W_C in manuscript
#                 "Continous-continous" W_D in manuscript
#                  "DGM" W_DGM in manuscript
#rho1 - parameter for continuous part of selection function W_B in manuscript, "Constant-continous"
#rho2 - parameter for continuous part of selection function W_C in manuscript, "Continous-constant"
#opt_method - string character for the desired optimizatin method, e.g., "L-BFGS-B"
#lower - vector of length 2 for the lower bound of the optimization if "L-BFGS-B" is used
#upper - vector of length 2 for the upper bound of the optimization if "L-BFGS-B" is used
#gam - parameter used in DGM and consequently to be used in DGM selection function for correct model specification

#Outputs
#mu_unadjusted = naive estimate of treatment effect, no ORB adjustment
#LR_mu_unadjusted_low = lower bound of PL CI for naive estimate of treatment effect
#LR_mu_unadjusted_up = upper bound of PL CI for naive estimate of treatment effect
#CI_unadjusted_low_WALD = lower bound of Wald CI for naive estimate of treatment effect
#CI_unadjusted_up_WALD = upper bound of Wald CI for naive estimate of treatment effect
#mu_adjusted_benefit = ORB-adjusted estimate of treatment effect
#LR_mu_adjusted_low = lower bound of PL CI for ORB-adjusted estimate of treatment effect
#LR_mu_adjusted_up = upper bound of PL CI for ORB-adjusted estimate of treatment effect
#CI_adjusted_benefit_low_WALD = lower bound of Wald CI for ORB-adjusted estimate of treatment effect
#CI_adjusted_benefit_up_WALD = upper bound of Wald CI for ORB-adjusted estimate of treatment effect
#tau_squared_unadjusted = naive estimate of heterogeneity variance
#LR_tau_squared_unadjusted_low = lower bound of PL CI for naive estimate of heterogeneity variance
#LR_tau_squared_unadjusted_up = upper bound of PL CI for naive estimate of heterogeneity variance
#tau_squared_adjusted = ORB-adjusted estimate of heterogeneity variance
#LR_tau_squared_adjusted_low = lower bound of PL CI for ORB-adjusted estimate of heterogeneity variance
#LR_tau_squared_adjusted_up = upper bound of PL CI for ORB-adjusted estimate of heterogeneity variance
#average_sigma_squared_unadjusted = average of imputed and reported variances with naive estimation
#sigma_squared_average_adjusted = average of imputed and reported variances with ORB-adjusted estimation


reORBadj <- function(a=NULL, 
                     c=NULL,
                     mu1=NULL, 
                     mu2=NULL, 
                     sd1=NULL, 
                     sd2=NULL,
                     y=NULL, 
                     s=NULL,
                     n1,
                     n2,
                     outcome,
                     init_param,
                     alpha_ben=NULL,
                     alpha_ben_one.sided = TRUE,
                     true.SE=NULL, 
                     LR.CI = FALSE,
                     Wald.CI = FALSE,
                     selection.benefit = "Copas.oneside",
                     rho1=3,
                     rho2=3,
                     opt_method="L-BFGS-B",
                     lower = c(-5, 0.00001),
                     upper = c(5,5),
                     gam = 1.5
) {
  
  #Can take in binary counts and calculate log RR: a, c
  #Means and calculate differences in means: y1, y2, sd1, sd2
  #Directly normally distributed effect measure: y, s
  
  #Beneficial outcome, i.e., positive direction of treatment
  
  #Selection functions for the probability of reporting as a function of pvalue
  #SS: Constant-constant
  #ST: Constant-continous
  #TS: Continous-constant
  #TT: Continous-continous
  #DGM: Corresponds to the function to use to generate ORB
  
  #If alpha_ben_one.sided=TRUE, we use the one-sided threshold 
  sel.ben <- selection.benefit
  
  #Parameters for continuous parts of selection functions
  rho1 <- rho1
  rho2 <- rho2
  
  #Parameter used in DGM and consequently to be used in DGM selection function for correct model specification
  gam <- gam
  
  #If FALSE, we do not calculate the Wald CI - they are numerically unstable sometimes
  if (Wald.CI){
    my.hessian <- TRUE
  } else{
    my.hessian <- FALSE
  }
  
  #Optimization method
  method <- opt_method
  lower <- lower
  upper <- upper
  
  
  #Binary input data to calculate log RR
  if (!is.null(a) & !is.null(c)){
    
    #Reported outcomes
    #Indecies where we do not have unrepoted outcomes, i.e., we have reported outcomes
    #If we turn C into numeric, the unreported become NA
    
    Rep_index <- which(!is.na(as.numeric(a)))
    HR_index <- which(a == "unrep")
    
    # a,c,n1,n2, n values for the reported studies
    a_rep <- as.numeric(a[Rep_index])
    c_rep <- as.numeric(c[Rep_index])
    n1_rep <- as.numeric(n1[Rep_index])
    n2_rep <- as.numeric(n2[Rep_index])
    
    if (length(a_rep == 0) | length(c_rep == 0) > 0){ #Continuity correction
      
      a_0_index <- c(which(a_rep == 0), which(c_rep == 0)) #Where the zero cell counts are
      a_rep[a_0_index] <- a_rep[a_0_index] + 0.5
      c_rep[a_0_index] <- c_rep[a_0_index] + 0.5
      n1_rep[a_0_index] <- n1_rep[a_0_index] + 0.5
      n2_rep[a_0_index] <- n2_rep[a_0_index] + 0.5 #Add 0.5 to the cell counts with 0
      
      a_0_both <- which(a_rep == 0.5 & c_rep == 0.5)
      
      if (length(a_0_both)>0){
        
        a_rep <- a_rep[-a_0_both]
        c_rep <- c_rep[-a_0_both]
        n1_rep <- n1_rep[-a_0_both]
        n2_rep <- n2_rep[-a_0_both]
        
      } else {
        
        a_rep <- a_rep
        c_rep <- c_rep
        n1_rep <- n1_rep
        n2_rep <- n2_rep
        
      }
      
    } else {
      
      a_rep <- a_rep
      c_rep <- c_rep
      n1_rep <- n1_rep
      n2_rep <- n2_rep
    }
    
    
    #How many studies are reported?
    N_rep <- length(Rep_index)
    
    #Unreported study sizes, we might have info from n1,n2 or just the total
    ntot <- as.numeric(n1) + as.numeric(n2)
    n_HR <- as.numeric(ntot[HR_index])
    
    
    #log RR and standard error
    logRR <- log((a_rep*n2_rep)/(c_rep*n1_rep))
    s <- sqrt(((n1_rep - a_rep)/(n1_rep*a_rep)) + ((n2_rep - c_rep)/(n2_rep*c_rep)))
    sigma_squared <- s^2
    
    
    
    #Imputed values of sigma squared for the unreported studies
    #K value based on the reported studies, see Copas et al. (2019)
    k <- sum(1/sigma_squared)/sum((n1_rep + n2_rep))
    
    #Mean differences as input data (continuous)
    #Same procedure
    
  } else if (!is.null(mu1) & !is.null(mu2) & !is.null(sd1) & !is.null(sd2)){
    
    Rep_index <- which(!is.na(as.numeric(mu1)))
    
    HR_index <- which(mu1 == "unrep")
      
    #Unreported study sizes, we might have info from n1,n2 or just the total
    ntot <- as.numeric(n1) +as.numeric(n2)
    n_HR <- as.numeric(ntot[HR_index])
    
    #mu1,mu2,n1,n2,n values for the reported studies
    mu1_rep <- as.numeric(mu1[Rep_index])
    mu2_rep <- as.numeric(mu2[Rep_index])
    sd1_rep <- as.numeric(sd1[Rep_index])
    sd2_rep <- as.numeric(sd2[Rep_index])
    n1_rep <- as.numeric(n1[Rep_index])
    n2_rep <- as.numeric(n2[Rep_index])
    
    #How many studies are reported?
    N_rep <- length(Rep_index)
    
    #Differenece in means
    #Standard errors given
    logRR <- mu1_rep - mu2_rep
    s <- sqrt((as.numeric(sd1_rep)^2)/(as.numeric(n1_rep)) + (as.numeric(sd2_rep)^2)/(as.numeric(n2_rep)))
    sigma_squared <- s^2
    
    k <- sum(1/sigma_squared)/sum((n1_rep + n2_rep))
    
    #We directly have the treatment effect and standard error
    
  } else if (!is.null(y) & !is.null(s)) {
    
    #Indecies where we have the reported outcomes and the unreported HR
    Rep_index <- which(!is.na(as.numeric(y)))
    
    HR_index <- which(y == "unrep")
    
    #Observed treatment effect, standard error^2, and sample sizes of reported outcomes
    logRR <- as.numeric(y[Rep_index])
    sigma_squared <- (as.numeric(s[Rep_index]))^2
    n1_rep <- as.numeric(n1[Rep_index])
    n2_rep <- as.numeric(n2[Rep_index])
    
    #Total sample size of unreported outcomes
    n_HR <- as.numeric(n1[HR_index]) + as.numeric(n2[HR_index])
    
    #k estimation, based on reported studies
    k <- sum(1/sigma_squared)/sum((n1_rep + n2_rep))
    
  } else {
    
    return("Error: invalid inputs. Input either a and c values or y1,sd1 and y2,sd2 values.")
  }
  
  
  #Possibility to pass the true SE to the function
  if (!is.null(true.SE)){
    
    sigma_squared_imputed <- (as.numeric(true.SE)[HR_index])^2
  } else {
    #Imputed variances for the HR studies
    #See Copas et al. (2019)
    sigma_squared_imputed <- 1/(k*n_HR)
    
  }
  
  #Average sigma squared value that is used when we do not adjust for ORB and when we do
  sigma_squared_average_unadjusted <- mean(sigma_squared)
  sigma_squared_average_adjusted <- mean(c(sigma_squared, sigma_squared_imputed))
  
  #Unadjusted log-likelihood function to be maximized
  f.u <- function(params, logRR, sigma_squared) {
    mu <- params[1]
    tau_squared <- params[2]
    if (tau_squared < 0 ){
      - Inf
    } else {
      
      -(1/2)*sum(log(sigma_squared + tau_squared) + ((logRR - mu)^2)/(sigma_squared + tau_squared))
    }
  }
  
  #Set initial values for mu and tau_squared
  init_params <- init_param
  
  #Maximize unadjusted function optim()
  if (method == "L-BFGS-B"){
    fit.u <- optim(init_params, f.u, logRR = logRR, sigma_squared = sigma_squared,
                   #method = "Nelder-Mead",
                   method=method,
                   lower = lower,
                   upper = upper,
                   control = list(fnscale = -1),
                   hessian=my.hessian)
  } else {
        fit.u <- optim(init_params, f.u, logRR = logRR, sigma_squared = sigma_squared,
                   method = method,
                   control = list(fnscale = -1),
                   hessian=my.hessian)
    
  }
  #Return unadjusted mu and tau_squared
  mle.u <- fit.u$par[1]
  mle.tau <- max(fit.u$par[2],0)
  
  #Beneficial outcome adjustment for ORB
  
  if(outcome == "benefit"){
    
    z_alpha.copas <- qnorm(1-alpha_ben/2) #two-sided threshold
    
    if (alpha_ben_one.sided == TRUE){ #one-sided threshold (reccomended for consistency with simulation process and literature)
      
      z_alpha <- qnorm(1-alpha_ben)
    } else {
      z_alpha <- qnorm(1-alpha_ben/2)
    }
    
    #Adjusted log-likelihood function for beneficial outcome to be maximized
    f.adj.b <- function(params, logRR, sigma_squared, sigma_squared_imputed) {
      mu <- params[1]
      tau_squared <- params[2]
      
      if(tau_squared < 0){
        - Inf
      } else {
        
        #The contribution from the reported studies is always present
        -(1/2)*sum(log(sigma_squared + tau_squared) + ((logRR - mu)^2)/(sigma_squared + tau_squared)) +
          
          
          if (length(sigma_squared_imputed) > 0) {
            
            if (sel.ben == "Constant.Constant"){
              
              #sum(log(pnorm((z_alpha*sqrt(sigma_squared_imputed) - mu)/sqrt(sigma_squared_imputed + tau_squared))))
              
              #Probability of reporting
              SS <- function(y, sigma_squared_imputed, alpha_ben) {
                
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                
                ifelse(p <= alpha_ben, 
                       1,
                       0)
              }
              
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, alpha_ben) {
                
                weight <- 1 - SS(y, sigma_squared_imputed, alpha_ben)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, alpha_ben), #change here April 2. added Vectorize
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
              
            } else if (sel.ben == "Constant.Continous") {
              #Probability of reporting
              TS <- function(y, sigma_squared_imputed, alpha_ben) {
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                ifelse(p <= alpha_ben, 
                       1,
                       (p^(-rho2))/(alpha_ben^(-rho2)))
              }
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, alpha_ben) {
                
                weight <- 1 - TS(y, sigma_squared_imputed, alpha_ben)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, alpha_ben), #change here April 2. added Vectorize
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
              
            } else if (sel.ben == "Continous.Constant") {
              
              #Probability of reporting
              ST <- function(y, sigma_squared_imputed, alpha_ben) {
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                ifelse(p <= alpha_ben, 
                       1-(p^rho1)/(alpha_ben^rho1),
                       0
                )
              }
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, alpha_ben) {
                
                weight <- 1 - ST(y, sigma_squared_imputed, alpha_ben)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, alpha_ben),
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
            } else if (sel.ben == "Continous.Continous") {
              #Probability of reporting
              TT <- function(y, sigma_squared_imputed, alpha_ben) {
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                ifelse(p <= alpha_ben, 
                       1 - (1-0.5)*(p^rho1)/(alpha_ben^rho1),
                       0.5*(p^(-rho2))/(alpha_ben^(-rho2))
                )
              }
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, alpha_ben) {
                
                weight <- 1 - TT(y, sigma_squared_imputed, alpha_ben)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, alpha_ben),
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
            
            } else if (sel.ben == "DGM") {
              
              #Probability of reporting
              DGM <- function(y, sigma_squared_imputed, gam) {
                
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                exp(-4*p^(gam))
              }
              
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, gam) {
                
                weight <- 1 - DGM(y, sigma_squared_imputed, gam)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, gam),
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
              
            } else {
              
              stop("Error: Invalid weight function specified. ")
            }
      
          } else {
            0  # Return 0 if sigma_squared_imputed is empty
          }
      }
    }
    #Maximize log-likelihood
    if (method == "L-BFGS-B"){
      
      fit.adj.b <- optim(init_params, f.adj.b, logRR = logRR, sigma_squared = sigma_squared, sigma_squared_imputed = sigma_squared_imputed,
                         method = method,
                         lower = lower,
                         upper = upper,
                         control = list(fnscale = -1),
                         
                         hessian=my.hessian)
    } else {
      
      fit.adj.b <- optim(init_params, f.adj.b, logRR = logRR, sigma_squared = sigma_squared, sigma_squared_imputed = sigma_squared_imputed,
                         method = method,
                         control = list(fnscale = -1),
                         hessian=my.hessian)
      
      
    }
    
    #Return adjusted mu and tau_squared
    mle.b <- fit.adj.b$par[1]
    mle.b.tau <- max(fit.adj.b$par[2],0)
    
    #LIKELIHOOD RATIO CONFIDENCE INTERVALS
    
    if (LR.CI){
      
      #Unadjusted
      z <- qchisq(1-alpha_ben, df=1) #3.841
      #Re-write log likelihood with two inputs instead of param = c(mu, tau_squared)
      ll.u <- function(mu, tau_squared, logRR, sigma_squared) {
        -(1/2)*sum(log(sigma_squared + tau_squared) + ((logRR - mu)^2)/(sigma_squared + tau_squared))
      }
      #Profile log-likelihood
      pl.u <- function(mu, logRR, sigma_squared) { #take in vector of mus
        res <- mu
        for (i in seq_along(mu)) { #for all these values of mu
          optimResult <- optim(par = init_param[2],
                               fn = function(tau_squared) ll.u(mu[i], tau_squared, logRR=logRR, sigma_squared = sigma_squared),
                               method = "Brent",
                               lower= 0.0001,
                               upper=10,
                               control = list(fnscale = -1))
          res[i] <- optimResult$value
        }
        return(res)
      }
      
      f <- function(mu, logRR, sigma_squared){
        pl.u(mu, logRR=logRR, sigma_squared=sigma_squared) - pl.u(mle.u, logRR=logRR, sigma_squared=sigma_squared) + 1/2*qchisq(0.95, df=1)
      }
      
      eps <- sqrt(.Machine$double.eps)
      lowerBound.u <- uniroot(f, interval = c(-5, mle.u), logRR=logRR, sigma_squared=sigma_squared)$root
      upperBound.u <- uniroot(f, interval = c( mle.u, 5), logRR=logRR, sigma_squared=sigma_squared)$root
      
      #Profile log-likelihood for tau squared
      pl.u.tau <- function(tau_squared, logRR, sigma_squared) { #take in vector of tau_squares
        
        res <- tau_squared
        for (i in seq_along(tau_squared)) { #for all these values of mu
          optimResult <- optim(par = init_param[1],
                               fn = function(mu) ll.u(tau_squared[i], mu, logRR=logRR, sigma_squared = sigma_squared),
                               method = "Brent",
                               lower= -5,
                               upper=5,
                               control = list(fnscale = -1))
          res[i] <- optimResult$value
        }
        return(res)
      }
      
      f.tau <- function(tau_squared, logRR, sigma_squared){
        pl.u.tau(tau_squared, logRR=logRR, sigma_squared=sigma_squared) - pl.u.tau(mle.tau, logRR=logRR, sigma_squared=sigma_squared) + 1/2*qchisq(0.95, df=1)
      }
      eps <- sqrt(.Machine$double.eps)
      lowerBound.u.tau <- max(uniroot(f.tau, interval = c(-10, mle.tau), logRR=logRR, sigma_squared=sigma_squared)$root,0)
      upperBound.u.tau <- max(uniroot(f.tau, interval = c( mle.tau, 10), logRR=logRR, sigma_squared=sigma_squared)$root,0)
      
      #Adjusted benefit
      
      #Re-write log likelihood with two inputs instead of param = c(mu, tau_squared)
      ll.b <- function(mu, tau_squared, logRR, sigma_squared, sigma_squared_imputed) {
        
        if(tau_squared < 0){
          - Inf
        } else {
          
        #The contribution from the reported studies is always present
        -(1/2)*sum(log(sigma_squared + tau_squared) + ((logRR - mu)^2)/(sigma_squared + tau_squared)) +
          
          if (length(sigma_squared_imputed) > 0) {
            if (sel.ben == "Constant.Constant"){
              
              #sum(log(pnorm((z_alpha*sqrt(sigma_squared_imputed) - mu)/sqrt(sigma_squared_imputed + tau_squared))))
              
              #Probability of reporting
              SS <- function(y, sigma_squared_imputed, alpha_ben) {
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                ifelse(p <= alpha_ben, 
                       1,
                       0)
              }
              
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, alpha_ben) {
                weight <- 1 - SS(y, sigma_squared_imputed, alpha_ben)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, alpha_ben), #change here April 2. added Vectorize
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
              
            } else if (sel.ben == "Constant.Continous") {
              
              #Probability of reporting
              TS <- function(y, sigma_squared_imputed, alpha_ben) {
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                ifelse(p <= alpha_ben, 
                       1,
                       (p^(-rho2))/(alpha_ben^(-rho2)))
              }
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, alpha_ben) {
                
                weight <- 1 - TS(y, sigma_squared_imputed, alpha_ben)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, alpha_ben), #change here April 2. added Vectorize
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
              
            } else if (sel.ben == "Continous.Constant") {
              
              #Probability of reporting
              ST <- function(y, sigma_squared_imputed, alpha_ben) {
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                
                ifelse(p <= alpha_ben, 
                       1-(p^rho1)/(alpha_ben^rho1),
                       0
                )
              }
              
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, alpha_ben) {
                
                weight <- 1 - ST(y, sigma_squared_imputed, alpha_ben)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, alpha_ben),
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
              
            } else if (sel.ben == "Continous.Continous") {
              
              #Probability of reporting
              TT <- function(y, sigma_squared_imputed, alpha_ben) {
                
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                
                ifelse(p <= alpha_ben, 
                       1 - (1-0.5)*(p^rho1)/(alpha_ben^rho1),
                       0.5*(p^(-rho2))/(alpha_ben^(-rho2))
                )
              }
              
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, alpha_ben) {
                
                weight <- 1 - TT(y, sigma_squared_imputed, alpha_ben)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, alpha_ben),
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
              
            } else if (sel.ben == "DGM") {
              
              #Probability of reporting
              DGM <- function(y, sigma_squared_imputed, gam) {
                
                p = pnorm(-y/sqrt(sigma_squared_imputed))
                
                exp(-4*p^(gam))
              }
              
              #Integrand
              integrand <- function(y, mu, tau_squared, sigma_squared_imputed, gam) {
                
                weight <- 1 - DGM(y, sigma_squared_imputed, gam)
                (1 / sqrt(2 * pi * (sigma_squared_imputed + tau_squared))) * exp(-0.5 * ((y - mu)^2 / (sigma_squared_imputed + tau_squared))) * weight
              }
              
              #log-lik contribution
              sum(log(sapply(sigma_squared_imputed, function(sigma_sq_imputed) {
                integrate(function(y) integrand(y, mu, tau_squared, sigma_sq_imputed, gam),
                          lower = -10, upper = 10, subdivisions = 200, stop.on.error=FALSE)$value
              })))
            } else {
              stop("Error: Invalid weight function specified. ")
            }
          } else {
            0  # Return 0 if sigma_squared_imputed is empty
          }
        }
      }
      #Adjusted profile log likelihood for mu
      pl.b <- function(mu, logRR, sigma_squared, sigma_squared_imputed) { #take in vector of mus
        res <- mu
        for (i in seq_along(mu)) { #for all these values of mu
          optimResult <- optim(par = init_param[2],
                               fn = function(tau_squared) ll.b(mu[i], tau_squared,
                                                               logRR=logRR,
                                                               sigma_squared = sigma_squared,
                                                               sigma_squared_imputed = sigma_squared_imputed),
                               method = "Brent", lower=0.00001, upper=10,
                               control = list(fnscale = -1))
          res[i] <- optimResult$value
        }
        return(res)
      }
      f.b <- function(mu, logRR, sigma_squared, sigma_squared_imputed){
        
        pl.b(mu, logRR=logRR, sigma_squared=sigma_squared, sigma_squared_imputed = sigma_squared_imputed) - pl.b(mle.b, logRR=logRR, sigma_squared=sigma_squared, sigma_squared_imputed = sigma_squared_imputed) + 1/2*qchisq(0.95, df=1)
      }
      lowerBound.b <- uniroot(f.b, interval = c(-10, mle.b), logRR=logRR,
                              sigma_squared=sigma_squared,
                              sigma_squared_imputed=sigma_squared_imputed)$root
      upperBound.b <- uniroot(f.b, interval = c(mle.b, 10), logRR=logRR,
                              sigma_squared=sigma_squared,
                              sigma_squared_imputed = sigma_squared_imputed)$root
      
      #Adjusted profile log likelihood for tau squared
      pl.b.tau <- function(tau_squared, logRR, sigma_squared, sigma_squared_imputed) { #take in vector of tau_squares
          res <- tau_squared
        for (i in seq_along(tau_squared)) { #for all these values of tau_squared
          optimResult <- optim(par = init_param[1],
                               fn = function(mu) ll.b(tau_squared[i], mu,
                                                      logRR=logRR,
                                                      sigma_squared = sigma_squared,
                                                      sigma_squared_imputed = sigma_squared_imputed), method = "Brent", lower=-5, upper=5,
           control = list(fnscale = -1))
          res[i] <- optimResult$value
        }
        return(res)
      }
      f.b.tau <- function(tau_squared, logRR, sigma_squared, sigma_squared_imputed){
        pl.b.tau(tau_squared, logRR=logRR, sigma_squared=sigma_squared, sigma_squared_imputed = sigma_squared_imputed) - pl.b.tau(mle.b.tau, logRR=logRR, sigma_squared=sigma_squared, sigma_squared_imputed = sigma_squared_imputed) + 1/2*qchisq(0.95, df=1)
      }
      lowerBound.b.tau <- 0
      
      tryCatch({
        
      lowerBound.b.tau <- 
        uniroot(f.b.tau, interval = c(-5, fit.adj.b$par[2]), logRR=logRR,
                              sigma_squared=sigma_squared, extendInt = "yes")$root
      }, error = function(e) {
        
        lowerBound.b.tau <- 0})
             
      upperBound.b.tau <- 0
      
      tryCatch({                        
      
      upperBound.b.tau <- 
        uniroot(f.b.tau, interval = c(fit.adj.b$par[2], 5), logRR=logRR,
                              sigma_squared=sigma_squared, sigma_squared_imputed=sigma_squared_imputed, extendInt="yes")$root
      }, error = function(e) {
        
        upperBound.b.tau <- 0})
      
      if (Wald.CI){
        #WALD CONFIDENCE INTERVALS
        a <- alpha_ben #for harm Copas et al use 99% conf level
        #Unadjusted
        fisher_info.u <- solve(-fit.u$hessian)
        s.u <- sqrt(diag(fisher_info.u)[1])
        ci.u <- fit.u$par[1] + qnorm(c(a/2, 1-a/2)) * s.u
        #Adjusted benefit
        fisher_info.adj.b <- solve(-fit.adj.b$hessian)
        s.adj.b <- sqrt(diag(fisher_info.adj.b)[1])
        ci.u.adj.b <- fit.adj.b$par[1] + qnorm(c(a/2, 1-a/2)) * s.adj.b

        return(list(mu_unadjusted = mle.u,
                    LR_mu_unadjusted_low = lowerBound.u,
                    LR_mu_unadjusted_up = upperBound.u,

                    CI_unadjusted_low_WALD = ci.u[1],
                    CI_unadjusted_up_WALD = ci.u[2],
                    
                    mu_adjusted_benefit = mle.b,
                    LR_mu_adjusted_low = lowerBound.b,
                    LR_mu_adjusted_up = upperBound.b,
                    
                    CI_adjusted_benefit_low_WALD = ci.u.adj.b[1],
                    CI_adjusted_benefit_up_WALD = ci.u.adj.b[2]
        ))
        
      } else {
        return(list(mu_unadjusted = mle.u,
                    LR_mu_unadjusted_low = lowerBound.u,
                    LR_mu_unadjusted_up = upperBound.u,
                    
                    mu_adjusted_benefit = mle.b,
                    LR_mu_adjusted_low = lowerBound.b,
                    LR_mu_adjusted_up = upperBound.b
        ))
      }
    } else {
      return(list(
        mu_unadjusted = mle.u,
        mu_adjusted_benefit = mle.b
      ))
    }
  } else {
    return("invalid outcome input")
  }
}
```

```{r, warning=FALSE}
resultLL_SeizureFree <- reORBadj(a = data_topiramate_unrep$T2,
                                 c = data_topiramate_unrep$C2,
                                 n1 = data_topiramate_unrep$N_t,
                                 n2 = data_topiramate_unrep$N_c,
                                 outcome = "benefit",
                                 init_param = c(0.7, 0.37),
                                 alpha_ben = 0.05,
                                 alpha_ben_one.sided = TRUE, 
                                 true.SE = NULL,
                                 LR.CI = TRUE,
                                 rho1 = 3,
                                 rho2 = 3,
                                 selection.benefit = "Constant.Constant",
                                 opt_method = "L-BFGS-B")

resultLC_SeizureFree <- reORBadj(a = data_topiramate_unrep$T2,
                                 c = data_topiramate_unrep$C2,
                                 n1 = data_topiramate_unrep$N_t,
                                 n2 = data_topiramate_unrep$N_c,
                                 outcome = "benefit",
                                 init_param = c(0.7, 0.37),
                                 alpha_ben = 0.05,
                                 alpha_ben_one.sided = TRUE, 
                                 true.SE = NULL,
                                 LR.CI = TRUE,
                                 rho1 = 3,
                                 rho2 = 3,
                                 selection.benefit = "Constant.Continous",
                                 opt_method = "L-BFGS-B")


resultCL_SeizureFree <- reORBadj(a = data_topiramate_unrep$T2,
                                 c = data_topiramate_unrep$C2,
                                 n1 = data_topiramate_unrep$N_t,
                                 n2 = data_topiramate_unrep$N_c,
                                 outcome = "benefit",
                                 init_param = c(0.7, 0.37),
                                 alpha_ben = 0.05,
                                 alpha_ben_one.sided = TRUE, 
                                 true.SE = NULL,
                                 LR.CI = TRUE,
                                 rho1 = 3,
                                 rho2 = 3,
                                 selection.benefit = "Continous.Constant",
                                 opt_method = "L-BFGS-B")

      
resultCC1_SeizureFree <- reORBadj(a = data_topiramate_unrep$T2,
                                  c = data_topiramate_unrep$C2,
                                  n1 = data_topiramate_unrep$N_t,
                                  n2 = data_topiramate_unrep$N_c,
                                  outcome = "benefit",
                                  init_param = c(0.7, 0.37),
                                  alpha_ben = 0.05,
                                  alpha_ben_one.sided = TRUE, 
                                  true.SE = NULL,
                                  LR.CI = TRUE,
                                  rho1 = 7,
                                  rho2 = 1.5,
                                  selection.benefit = "Continous.Continous",
                                  opt_method = "L-BFGS-B")
          
resultCC2_SeizureFree <- reORBadj(a = data_topiramate_unrep$T2,
                                  c = data_topiramate_unrep$C2,
                                  n1 = data_topiramate_unrep$N_t,
                                  n2 = data_topiramate_unrep$N_c,
                                  outcome = "benefit",
                                  init_param = c(0.7, 0.37),
                                  alpha_ben = 0.05,
                                  alpha_ben_one.sided = TRUE, 
                                  true.SE = NULL,
                                  LR.CI = TRUE,
                                  rho1 = 1.5,
                                  rho2 = 7,
                                  selection.benefit = "Continous.Continous",
                                  opt_method = "L-BFGS-B")
```

```{r}
source("Code/00.Functions.R")
o <- 2
deltas <- c(0, 0.5, 1.3)
measures <- c("RR")
m_imputations <- 1000

#Loop 0: iterate over the two outcomes
res_uni_plot <- list()   # reset per outcome, otherwise the O2 file also contains the O1 rows
  # Loop 1: Iterate over measures first and impute once per measure
  for (m in measures) {
    
    theta_cols <- paste0("log_", m, o)
    se_cols <- paste0("se_", m, o)
    
    #cat(sprintf("Generating imputed data for Measure = %s\n", m))
    
    # Run imputation ONCE here. The random pool is now locked in.
    mi <- run_univariate_imputation(
      data = data_topiramate,
      theta_col = theta_cols,
      se_col = se_cols,
      m = m_imputations
    )
    
    # Extract the static Naive estimate for this measure
    naive_df <- data.frame(
      Approach = "Naive estimate",
      Estimate = as.numeric(mi$res_naive$beta),
      SE       = mi$res_naive$se,
      CI_Lower = mi$res_naive$ci.lb,
      CI_Upper = mi$res_naive$ci.ub
    )
    
    # refit the imputed datasets once, reused for every delta and selection type
    fits_uni <- fit_imputations_uni(mi)
   # failed_refits[paste0("Plot uni ", m, " O", o)] <- attr(fits_uni, "failed.proportion")
    
    # Loop 2: Now test different deltas using the same imputed data
    for (delta in deltas) {
      
      #cat(sprintf("  -> Calculating adjustments for delta = %s\n", delta))
      
      # Importance sampling calculations over the static 'mi' object
      adj_eff <- adj_univariate(mi,
                                delta = delta,
                                select_type = "effect",
                                track.ess = FALSE,
                                fits = fits_uni)
      
      adj_z   <- adj_univariate(mi,
                                delta = delta,
                                select_type = "zscore",
                                track.ess = FALSE,
                                fits = fits_uni)
      
      # Stack the results
      tmp <- rbind(naive_df, adj_eff, adj_z)
      
      # Add metadata
      tmp$Measure   <- paste0("log ", m)
      tmp$Selection <- delta  # Saved as numeric directly to avoid your earlier character bug!
      
      # Append to list
      res_uni_plot[[length(res_uni_plot) + 1]] <- tmp
    }
  }
  
 plot_uni_df <- do.call(rbind,
                        res_uni_plot)
  
  # bring data into wide format
 naive_df <- plot_uni_df %>%
    filter(Approach == "Naive estimate") %>%
    dplyr::select(Selection,
                  Estimate_unadjusted = Estimate,
                  CI_unadjusted_lower = CI_Lower,
                  CI_unadjusted_upper = CI_Upper)
  
  adjusted_df <- plot_uni_df %>%
    filter(Approach != "Naive estimate") %>%
    # Create the Z_score column your plot expects (TRUE if zscore, FALSE if effect)
    mutate(Z_score = ifelse(Approach == "Selection on zscore", TRUE, FALSE)) %>%
    dplyr::select(Selection, Z_score,
                  estimate_logRR = Estimate,
                  ci_lower_logRR = CI_Lower,
                  ci_upper_logRR = CI_Upper)
  
final_uni_df <- adjusted_df %>%
    left_join(naive_df, by = c("Selection"))
  
df_naive_uni <- naive_df %>%
  slice(1) %>%
  transmute(
    Model      = "Naive Univariate Estimate",
    logRR      = Estimate_unadjusted,
    CI_low_log = CI_unadjusted_lower,
    CI_up_log  = CI_unadjusted_upper,
    RR         = exp(logRR),
    CI_low_RR  = exp(CI_low_log),
    CI_up_RR   = exp(CI_up_log)
  )
```

```{r}
res_biv_df <- list()
rhos <- c("pearson")
deltas <- c(0, 0.5, 1.3) 
m_imputations <- 1000

set.seed(1)

# loop over the rhos 
for (rho in rhos) {
  
  #loop over the two measures (here we dont loop for the outcomes since they are processed together)
  for (m in measures) {
    
   # cat(sprintf("\n--- Running Bivariate Imputation Pool: Measure = %s, correlation setting = %s ---\n", m, rho))
    
    theta_cols <- paste0("log_", m, c(1, 2))
    se_cols <- paste0("se_", m, c(1, 2))
    
    # Run imputation
    mi_biv <- run_bivariate_imputation(
      data = data_topiramate, 
      theta_cols = theta_cols, 
      se_cols = se_cols, 
      rho_w = rho, 
      m = m_imputations
    )
    
    # create naive df similar to the one produced by adj_bivariate
    naive_df <- data.frame(
      Outcome   = c("O1", "O2"),
      Approach  = "Naive estimate",
      Estimate  = as.numeric(mi_biv$res_naive$beta),
      SE        = sqrt(diag(mi_biv$res_naive$vb)),
      CI_Lower  = mi_biv$res_naive$ci.lb,
      CI_Upper  = mi_biv$res_naive$ci.ub
    )
    
    # refit the imputed datasets once, reused for every delta and selection type
    fits_biv <- fit_imputations_biv(mi_biv)
    #failed_refits[paste0("Plot biv ", m, " rho_w=", rho)] <- mean(sapply(fits_biv, is.null))
    
    for(delta in deltas) {
      
     # cat(sprintf("  -> Calculating Bivariate Adjustments for delta = %s\n", delta))
      
      # Calculate both Adjustments (each return a 2-row dataframe for O1 and O2)
      adj_eff <- adj_bivariate(mi_biv, 
                               delta = delta, 
                               select_type = "effect",
                               track.ess = FALSE, 
                               track.failed.proportion = FALSE,
                               fits = fits_biv)
      
      adj_z   <- adj_bivariate(mi_biv, 
                               delta = delta, 
                               select_type = "zscore", 
                               track.ess = FALSE, 
                               track.failed.proportion = FALSE,
                               fits = fits_biv)
      
      # stack them
      tmp <- rbind(naive_df,
                   adj_eff,
                   adj_z)
      
      #add explaining columns
      tmp$Correlation <- paste0(rho)
      tmp$Measure     <- paste0("log ", m)
      tmp$Selection   <- delta
      
      res_biv_df[[length(res_biv_df) + 1]] <- tmp
    }
  }
}

plot_biv_df <- do.call(rbind,
                       res_biv_df)
# Reshape wide
naive_part <- plot_biv_df %>%
    filter(Approach == "Naive estimate") %>%
    dplyr::select(Outcome, Measure, Selection, Correlation,
           Estimate_unadjusted = Estimate,
           CI_unadjusted_lower = CI_Lower,
           CI_unadjusted_upper = CI_Upper)
  
plot_biv_df <- plot_biv_df %>%
    filter(Approach != "Naive estimate") %>%
    mutate(
      Z_score = (Approach == "Bivariate Selection on zscore")
    ) %>%
    dplyr::select(Outcome, Measure, Selection, Z_score, Correlation,
           Estimate_adjusted = Estimate, 
           SE_adjusted       = SE,
           CI_adjusted_lower = CI_Lower, 
           CI_adjusted_upper = CI_Upper) %>%
    left_join(naive_part, by = c("Selection", "Measure", "Correlation", "Outcome"))
 
 plot_biv_df_O2 <- subset(plot_biv_df, Outcome == "O2")
 
# Format Naive Bivariate row
df_naive_biv <- naive_part %>%
  filter(Outcome == "O2") %>%
  slice(1) %>%
  transmute(
    Model      = "Naive Bivariate Estimate",
    logRR      = Estimate_unadjusted,
    CI_low_log = CI_unadjusted_lower,
    CI_up_log  = CI_unadjusted_upper,
    RR         = exp(logRR),
    CI_low_RR  = exp(CI_low_log),
    CI_up_RR   = exp(CI_up_log)
  )
```

```{r}
# Kirkham et al. (2012)
# Bivariate multivariate meta-analysis for outcome reporting bias
fit_kirkham_bivariate <- function(data,
                                  rho_w = rho_w,
                                  method = "REML") {
  # Create long-format data
  df_long <- bind_rows(
    data %>%
      transmute(Study_id = Study_id,
                outcome  = "O1",
                yi       = log_RR1,
                sei      = se_RR1),
    data %>%
      transmute(Study_id = Study_id,
                outcome  = "O2",
                yi       = log_RR2,
                sei      = se_RR2)
  ) %>%
    mutate(outcome = factor(outcome, levels = c("O1", "O2"))) %>%
    arrange(Study_id, outcome)
  # Identify observed outcomes
  df_obs <- df_long %>%
    filter(!is.na(yi), !is.na(sei))

  # Check that both outcomes are available
  if (!all(c("O1", "O2") %in% unique(df_obs$outcome))) {
    stop("Both outcomes must have at least one reported study.")
  }
  # Construct within-study covariance matrix
  # Only reported outcomes are included.
  # For studies reporting both outcomes:
  # Cov(Y_i1, Y_i2) = rho_w * SE_i1 * SE_i2
  studies <- unique(df_obs$Study_id)
  V_blocks <- vector("list", length(studies))
  names(V_blocks) <- studies
  for (s in studies) {
    d <- df_obs[df_obs$Study_id == s, ]
    # Order O1, O2
    d <- d[order(d$outcome), ]
    if (nrow(d) == 2) {
      se1 <- d$sei[d$outcome == "O1"]
      se2 <- d$sei[d$outcome == "O2"]
      V_blocks[[as.character(s)]] <-
        matrix(
          c(se1^2,
            rho_w * se1 * se2,
            rho_w * se1 * se2,
            se2^2), 
          nrow = 2, byrow = TRUE
        )
    } else {
      # Only one outcome reported
      V_blocks[[as.character(s)]] <-  matrix(d$sei^2, nrow = 1, ncol = 1)
    }
  }
  # Combine blocks into full V matrix
  V <- as.matrix(Matrix::bdiag(V_blocks))
  # Ensure the order of rows in df_obs corresponds to V
  df_obs <- df_obs %>%
    arrange(Study_id, outcome)
  # Fit bivariate random-effects meta-analysis
  # This is the Kirkham multivariate approach:information from O1 contributes to 
  # estimation of O2 through the within-study and between-study correlations.
  fit <- metafor::rma.mv(yi = yi,
                         V = V,
                         mods = ~ outcome - 1,
                         random = ~ outcome | Study_id,
                         struct = "UN",
                         data = df_obs,
                         method = method,
                         control = list(rel.tol = 1e-8, maxiter = 1000))
  # 7. Extract pooled estimates
  beta <- as.numeric(coef(fit))
  se   <- fit$se
  ci_lb <- fit$ci.lb
  ci_ub <- fit$ci.ub
  result <- data.frame(Approach = "Kirkham et al. (2012)",
                       Outcome = c("O1", "O2"),
                       Estimate = beta,
                       SE = se,
                       CI_Lower = ci_lb,
                       CI_Upper = ci_ub) %>%
    mutate(RR = exp(Estimate),
           CI_Lower_RR = exp(CI_Lower),
           CI_Upper_RR = exp(CI_Upper))
  return(
    list(fit = fit)
  )
}

complete <- data_topiramate %>%
  filter(!is.na(log_RR1),
         !is.na(log_RR2))

rho_w <- cor(
  complete$log_RR1,
  complete$log_RR2,
  method = "pearson"
)
  
kirkham_res <- fit_kirkham_bivariate(
  data = data_topiramate,
  rho_w = rho_w
)

# Extract Outcome 2 (Seizure Freedom, which corresponds to outcomeO2)
kirkham_fit <- kirkham_res$fit

# Identify index for Outcome 2 in rma.mv coefficients
idx_o2 <- which(names(coef(kirkham_fit)) == "outcomeO2")

# Format Kirkham result as a 1-row data frame matching your other models
df_kirkham <- data.frame(
  Model      = "Kirkham et al. (2012)",
  logRR      = as.numeric(coef(kirkham_fit)[idx_o2]),
  CI_low_log = as.numeric(kirkham_fit$ci.lb[idx_o2]),
  CI_up_log  = as.numeric(kirkham_fit$ci.ub[idx_o2]),
  RR         = exp(as.numeric(coef(kirkham_fit)[idx_o2])),
  CI_low_RR  = exp(as.numeric(kirkham_fit$ci.lb[idx_o2])),
  CI_up_RR   = exp(as.numeric(kirkham_fit$ci.ub[idx_o2]))
)
```


```{r}
#  Format the Logistic ORB results
df_logistic_biv <- plot_biv_df_O2 %>%
  mutate(
    stat_label = ifelse(Z_score == TRUE, "z", "\u03b8\u0302"),
    Model = paste0("Biv-MI-ORB (\u03b4 = ", Selection, ", s = ", stat_label, ")"),
    logRR = Estimate_adjusted,
    CI_low_log = CI_adjusted_lower,
    CI_up_log  = CI_adjusted_upper,
    RR         = exp(logRR),
    CI_low_RR  = exp(CI_low_log),
    CI_up_RR   = exp(CI_up_log)
  ) %>%
  dplyr::select(Model, logRR, CI_low_log, CI_up_log, RR, CI_low_RR, CI_up_RR)

#  Format the Logistic ORB results
df_logistic_formatted <- final_uni_df %>%
  mutate(
    stat_label = ifelse(Z_score == TRUE, "z", "\u03b8\u0302"),
    Model = paste0("Uni-MI-ORB (\u03b4 = ", Selection, ", s = ", stat_label, ")"),
    logRR = estimate_logRR,
    CI_low_log = ci_lower_logRR,
    CI_up_log  = ci_upper_logRR,
    RR         = exp(logRR),
    CI_low_RR  = exp(CI_low_log),
    CI_up_RR   = exp(CI_up_log)
  ) %>%
  dplyr::select(Model, logRR, CI_low_log, CI_up_log, RR, CI_low_RR, CI_up_RR)

#  Results list for the existing models
results_list <- list("Copas (ORBIT Adjusted) (FE)"        = copas_result,
                     "Saracini: Piecewise constant"       = resultLL_SeizureFree,
                     "Saracini: Constant-Decreasing"      = resultLC_SeizureFree,
                     "Saracini: Decreasing-Constant"      = resultCL_SeizureFree,
                     "Saracini: Piecewise Decreasing (1)" = resultCC2_SeizureFree,
                     "Saracini: Piecewise Decreasing (2)" = resultCC1_SeizureFree)

# Extraction helper
extract_model_estimates <- function(res, name) {
  if (name == "Copas (ORBIT Adjusted) (FE)") {
    mu  <- res$estimate_logRR
    low <- res$ci_lower_logRR
    up  <- res$ci_upper_logRR
  } else {
    mu  <- res$mu_adjusted_benefit
    low <- res$LR_mu_adjusted_low
    up  <- res$LR_mu_adjusted_up
  }
  
  data.frame(Model      = name,
             logRR      = mu,
             CI_low_log = low,
             CI_up_log  = up,
             RR         = exp(mu),
             CI_low_RR  = exp(low),
             CI_up_RR   = exp(up))
}

df_other <- imap_dfr(results_list,
                     extract_model_estimates)

#  Stack all models together
df_all_models <- bind_rows(df_naive_uni,
                           df_other, 
                           df_logistic_formatted,
                           df_naive_biv,
                           df_kirkham,
                           df_logistic_biv)

# Add a category variable for grouped coloring
df_all_models <- df_all_models |>
  mutate(
    Category = case_when(
      grepl("Naive", Model) ~ "Naive",
      grepl("Copas", Model)      ~ "Copas",
      grepl("Saracini", Model)   ~ "Saracini & Held",
      grepl("Uni-MI-ORB", Model)   ~ "Uni-MI-ORB",
      grepl("Biv-MI-ORB", Model)   ~ "Biv-MI-ORB",
      grepl("Kirkham", Model)      ~ "Kirkham",
      TRUE                       ~ "Other"
    ),
    Model = factor(Model, levels = rev(unique(Model)))
  )
```

```{r}
# Create label column "RR [CI_low, CI_up]"
df_plot <- df_all_models |>
  mutate(
    # Format text: e.g. "3.22 [1.27, 8.65]"
    label_text = sprintf("%.2f [%.2f, %.2f]", RR, CI_low_RR, CI_up_RR),
    # Preserve vertical ordering
    Model = factor(Model, levels = rev(unique(Model)))
  )

# Determine maximum upper CI limit to dynamically position labels
x_min <- min(df_plot$CI_low_log, na.rm = TRUE)
x_max <- max(df_plot$CI_up_log, na.rm = TRUE)

x_range <- x_max - x_min

ggplot(df_plot, aes(x = logRR, y = Model, color = Category)) +
  # Reference line at No Effect (RR = 1)
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray60") +
  # Error bars and point estimates
  geom_errorbarh(aes(xmin = CI_low_log, xmax = CI_up_log), width = 0.25, linewidth = 0.8) +
  geom_point(shape = 18, size = 3.5) +
  # Logarithmic scale with margin space for the text column
  scale_x_continuous(limits = c(x_min - 0.05 * x_range,x_max + 0.05 * x_range)) +
  # Allow text to sit outside default clipping area if needed
  coord_cartesian(clip = "off") +
  labs(x = "Log RR", y = NULL, color = " ") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    legend.position  = "none",
    plot.title       = element_text(face = "bold", hjust = 0),
    axis.text.y      = element_text(face = "bold", color = "black"))

ggsave("Plots_Paper/Forestplot_Comparison_O2.png", width = 10, height = 6)
```

### for seizure reduction

```{r}
# copas Orbit approach
copas_result_O1 <- copas_orb_adjustment(data_topiramate,
                                        theta_col = "log_RR1", 
                                        se_col    = "se_RR1", 
                                        risk_col  = "orbit_out1", )

```

```{r, warning=FALSE}
resultLL_SeizureRed <- reORBadj(a = data_topiramate_unrep$T1,
                                c = data_topiramate_unrep$C1,
                                n1 = data_topiramate_unrep$N_t,
                                n2 = data_topiramate_unrep$N_c,
                                outcome = "benefit",
                                init_param = c(0.7, 0.37),
                                alpha_ben = 0.05,
                                alpha_ben_one.sided = TRUE, 
                                true.SE = NULL,
                                LR.CI = TRUE,
                                rho1 = 3,
                                rho2 = 3,
                                selection.benefit = "Constant.Constant",
                                opt_method = "L-BFGS-B")

resultLC_SeizureRed <- reORBadj(a = data_topiramate_unrep$T1,
                                c = data_topiramate_unrep$C1,
                                n1 = data_topiramate_unrep$N_t,
                                n2 = data_topiramate_unrep$N_c,
                                outcome = "benefit",
                                init_param = c(0.7, 0.37),
                                alpha_ben = 0.05,
                                alpha_ben_one.sided = TRUE, 
                                true.SE = NULL,
                                LR.CI = TRUE,
                                rho1 = 3,
                                rho2 = 3,
                                selection.benefit = "Constant.Continous",
                                opt_method = "L-BFGS-B")


resultCL_SeizureRed <- reORBadj(a = data_topiramate_unrep$T1,
                                c = data_topiramate_unrep$C1,
                                n1 = data_topiramate_unrep$N_t,
                                n2 = data_topiramate_unrep$N_c,
                                outcome = "benefit",
                                init_param = c(0.7, 0.37),
                                alpha_ben = 0.05,
                                alpha_ben_one.sided = TRUE, 
                                true.SE = NULL,
                                LR.CI = TRUE,
                                rho1 = 3,
                                rho2 = 3,
                                selection.benefit = "Continous.Constant",
                                opt_method = "L-BFGS-B")

      
resultCC1_SeizureRed <- reORBadj(a = data_topiramate_unrep$T1,
                                 c = data_topiramate_unrep$C1,
                                 n1 = data_topiramate_unrep$N_t,
                                 n2 = data_topiramate_unrep$N_c,
                                 outcome = "benefit",
                                 init_param = c(0.7, 0.37),
                                 alpha_ben = 0.05,
                                 alpha_ben_one.sided = TRUE, 
                                 true.SE = NULL,
                                 LR.CI = TRUE,
                                 rho1 = 7,
                                 rho2 = 1.5,
                                 selection.benefit = "Continous.Continous",
                                 opt_method = "L-BFGS-B")
          
resultCC2_SeizureRed <- reORBadj(a = data_topiramate_unrep$T1,
                                 c = data_topiramate_unrep$C1,
                                 n1 = data_topiramate_unrep$N_t,
                                 n2 = data_topiramate_unrep$N_c,
                                 outcome = "benefit",
                                 init_param = c(0.7, 0.37),
                                 alpha_ben = 0.05,
                                 alpha_ben_one.sided = TRUE, 
                                 true.SE = NULL,
                                 LR.CI = TRUE,
                                 rho1 = 1.5,
                                 rho2 = 7,
                                 selection.benefit = "Continous.Continous",
                                 opt_method = "L-BFGS-B")
```

```{r}
# Identify index for Outcome 2 in rma.mv coefficients
idx_o1 <- which(names(coef(kirkham_fit)) == "outcomeO1")

# Format Kirkham result as a 1-row data frame matching your other models
df_kirkham_O1 <- data.frame(
  Model      = "Kirkham et al. (2012)",
  logRR      = as.numeric(coef(kirkham_fit)[idx_o1]),
  CI_low_log = as.numeric(kirkham_fit$ci.lb[idx_o1]),
  CI_up_log  = as.numeric(kirkham_fit$ci.ub[idx_o1]),
  RR         = exp(as.numeric(coef(kirkham_fit)[idx_o1])),
  CI_low_RR  = exp(as.numeric(kirkham_fit$ci.lb[idx_o1])),
  CI_up_RR   = exp(as.numeric(kirkham_fit$ci.ub[idx_o1]))
)
```

```{r}
o <- 1
res_uni_plot <- list()   # reset per outcome, otherwise the O2 file also contains the O1 rows
  # Loop 1: Iterate over measures first and impute once per measure
  for (m in measures) {
    
    theta_cols <- paste0("log_", m, o)
    se_cols <- paste0("se_", m, o)
    
   # cat(sprintf("Generating imputed data for Measure = %s\n", m))
    
    # Run imputation ONCE here. The random pool is now locked in.
    mi <- run_univariate_imputation(
      data = data_topiramate,
      theta_col = theta_cols,
      se_col = se_cols,
      m = m_imputations
    )
    
    # Extract the static Naive estimate for this measure
    naive_df <- data.frame(
      Approach = "Naive estimate",
      Estimate = as.numeric(mi$res_naive$beta),
      SE       = mi$res_naive$se,
      CI_Lower = mi$res_naive$ci.lb,
      CI_Upper = mi$res_naive$ci.ub
    )
    
    # refit the imputed datasets once, reused for every delta and selection type
    fits_uni <- fit_imputations_uni(mi)
    #failed_refits[paste0("Plot uni ", m, " O", o)] <- attr(fits_uni, "failed.proportion")
    
    # Loop 2: Now test different deltas using the same imputed data
    for (delta in deltas) {
      
      #cat(sprintf("  -> Calculating adjustments for delta = %s\n", delta))
      
      # Importance sampling calculations over the static 'mi' object
      adj_eff <- adj_univariate(mi,
                                delta = delta,
                                select_type = "effect",
                                track.ess = FALSE,
                                fits = fits_uni)
      
      adj_z   <- adj_univariate(mi,
                                delta = delta,
                                select_type = "zscore",
                                track.ess = FALSE,
                                fits = fits_uni)
      
      # Stack the results
      tmp <- rbind(naive_df, adj_eff, adj_z)
      
      # Add metadata
      tmp$Measure   <- paste0("log ", m)
      tmp$Selection <- delta  # Saved as numeric directly to avoid your earlier character bug!
      
      # Append to list
      res_uni_plot[[length(res_uni_plot) + 1]] <- tmp
    }
  }
plot_uni_df_O1 <- do.call(rbind,
                          res_uni_plot)
  
# bring data into wide format
naive_df_O1 <- plot_uni_df_O1 %>%
    filter(Approach == "Naive estimate") %>%
    dplyr::select(Selection,
                  Estimate_unadjusted = Estimate,
                  CI_unadjusted_lower = CI_Lower,
                  CI_unadjusted_upper = CI_Upper)
  
adjusted_df_O1 <- plot_uni_df_O1 %>%
    filter(Approach != "Naive estimate") %>%
    # Create the Z_score column your plot expects (TRUE if zscore, FALSE if effect)
    mutate(Z_score = ifelse(Approach == "Selection on zscore", TRUE, FALSE)) %>%
    dplyr::select(Selection, Z_score,
                  estimate_logRR = Estimate,
                  ci_lower_logRR = CI_Lower,
                  ci_upper_logRR = CI_Upper)
  
final_uni_df_O1 <- adjusted_df_O1 %>%
    left_join(naive_df_O1, by = c("Selection"))
  
df_naive_uni_O1 <- naive_df_O1 %>%
  slice(1) %>%
  transmute(
    Model      = "Naive Univariate Estimate",
    logRR      = Estimate_unadjusted,
    CI_low_log = CI_unadjusted_lower,
    CI_up_log  = CI_unadjusted_upper,
    RR         = exp(logRR),
    CI_low_RR  = exp(CI_low_log),
    CI_up_RR   = exp(CI_up_log)
  )
```



```{r}

plot_biv_df_O1 <- subset(plot_biv_df, Outcome == "O1")
 
# Format Naive Bivariate row
df_naive_biv_O1 <- naive_part %>%
  filter(Outcome == "O1") %>%
  slice(1) %>%
  transmute(
    Model      = "Naive Bivariate Estimate",
    logRR      = Estimate_unadjusted,
    CI_low_log = CI_unadjusted_lower,
    CI_up_log  = CI_unadjusted_upper,
    RR         = exp(logRR),
    CI_low_RR  = exp(CI_low_log),
    CI_up_RR   = exp(CI_up_log)
  )
```


```{r}
#  Format the Logistic ORB results
df_logistic_biv_O1 <- plot_biv_df_O1 %>%
  mutate(
    stat_label = ifelse(Z_score == TRUE, "z", "\u03b8\u0302"),
    Model = paste0("Biv-MI-ORB (\u03b4 = ", Selection, ", s = ", stat_label, ")"),
    logRR = Estimate_adjusted,
    CI_low_log = CI_adjusted_lower,
    CI_up_log  = CI_adjusted_upper,
    RR         = exp(logRR),
    CI_low_RR  = exp(CI_low_log),
    CI_up_RR   = exp(CI_up_log)
  ) %>%
  dplyr::select(Model, logRR, CI_low_log, CI_up_log, RR, CI_low_RR, CI_up_RR)

#  Format the Logistic ORB results
df_logistic_formatted <- final_uni_df_O1 %>%
  mutate(
    stat_label = ifelse(Z_score == TRUE, "z", "\u03b8\u0302"),
    Model = paste0("Uni-MI-ORB (\u03b4 = ", Selection, ", s = ", stat_label, ")"),
    logRR = estimate_logRR,
    CI_low_log = ci_lower_logRR,
    CI_up_log  = ci_upper_logRR,
    RR         = exp(logRR),
    CI_low_RR  = exp(CI_low_log),
    CI_up_RR   = exp(CI_up_log)
  ) %>%
  dplyr::select(Model, logRR, CI_low_log, CI_up_log, RR, CI_low_RR, CI_up_RR)

#  Results list for the existing models
results_list <- list("Copas (ORBIT Adjusted) (FE)"        = copas_result_O1,
                     "Saracini: Piecewise constant"       = resultLL_SeizureRed,
                     "Saracini: Constant-Decreasing"      = resultLC_SeizureRed,
                     "Saracini: Decreasing-Constant"      = resultCL_SeizureRed,
                     "Saracini: Piecewise Decreasing (1)" = resultCC2_SeizureRed,
                     "Saracini: Piecewise Decreasing (2)" = resultCC1_SeizureRed)

# Extraction helper
extract_model_estimates <- function(res, name) {
  if (name == "Copas (ORBIT Adjusted) (FE)") {
    mu  <- res$estimate_logRR
    low <- res$ci_lower_logRR
    up  <- res$ci_upper_logRR
  } else {
    mu  <- res$mu_adjusted_benefit
    low <- res$LR_mu_adjusted_low
    up  <- res$LR_mu_adjusted_up
  }
  
  data.frame(Model      = name,
             logRR      = mu,
             CI_low_log = low,
             CI_up_log  = up,
             RR         = exp(mu),
             CI_low_RR  = exp(low),
             CI_up_RR   = exp(up))
}

df_other <- imap_dfr(results_list,
                     extract_model_estimates)

#  Stack all models together
df_all_models <- bind_rows(df_naive_uni_O1,
                           df_other, 
                           df_logistic_formatted,
                           df_naive_biv_O1,
                           df_kirkham_O1,
                           df_logistic_biv_O1)

# Add a category variable for grouped coloring
df_all_models <- df_all_models |>
  mutate(
    Category = case_when(
      grepl("Naive", Model) ~ "Naive",
      grepl("Copas", Model)      ~ "Copas",
      grepl("Saracini", Model)   ~ "Saracini & Held",
      grepl("Uni-MI-ORB", Model)   ~ "Uni-MI-ORB",
      grepl("Biv-MI-ORB", Model)   ~ "Biv-MI-ORB",
      grepl("Kirkham", Model)      ~ "Kirkham",
      TRUE                       ~ "Other"
    ),
    Model = factor(Model, levels = rev(unique(Model)))
  )
```

```{r}
# Create label column "RR [CI_low, CI_up]"
df_plot <- df_all_models |>
  mutate(
    # Format text: e.g. "3.22 [1.27, 8.65]"
    label_text = sprintf("%.2f [%.2f, %.2f]", RR, CI_low_RR, CI_up_RR),
    # Preserve vertical ordering
    Model = factor(Model, levels = rev(unique(Model)))
  )

ggplot(df_plot, aes(x = logRR, y = Model, color = Category)) +
  # Reference line at No Effect (RR = 1)
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray60") +
  # Error bars and point estimates
  geom_errorbarh(aes(xmin = CI_low_log, xmax = CI_up_log), width = 0.25, linewidth = 0.8) +
  geom_point(shape = 18, size = 3.5) +
  # Logarithmic scale with margin space for the text column
  #scale_x_continuous(limits = c(x_min - 0.05 * x_range,x_max + 0.05 * x_range)) +
  # Allow text to sit outside default clipping area if needed
  coord_cartesian(clip = "off") +
  labs(x = "Log RR", y = NULL, color = " ") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    legend.position  = "none",
    plot.title       = element_text(face = "bold", hjust = 0),
    axis.text.y      = element_text(face = "bold", color = "black"))

ggsave("Plots_Paper/Forestplot_Comparison_O1.png", width = 10, height = 6)
```