---
title: "03.Application_plots.Rmd"
author: "Cora Burgwinkel"
date: "2026-05-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# load libaries
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
```

# Plot Univariate for seizure reduction

```{r, fig.width = 10, fig.height = 10}
final_uni_df_O1 <- read.csv2("Data/data_uni_df_O1.csv", sep = ",")

final_uni_df_O1 <- final_uni_df_O1 %>%
  mutate(across(c(Selection, Estimate_adjusted, Estimate_unadjusted,
                   CI_adjusted_lower, CI_adjusted_upper, Estimate_unadjusted,
                  CI_unadjusted_lower, CI_unadjusted_upper), as.numeric))

# plot the different z-scores for unadjusted and adjusted estimates
ggplot(data = final_uni_df_O1, aes(x = as.numeric(Selection))) +
  # Add ribbons for confidence intervals
  geom_ribbon(aes(ymin = CI_adjusted_lower, ymax = CI_adjusted_upper, fill = "Adjusted CI"), alpha = 0.2) +
  geom_ribbon(aes(ymin = CI_unadjusted_lower, ymax = CI_unadjusted_upper, fill = "Unadjusted CI"), alpha = 0.1) +
  # Add adjusted estimate line and point
  geom_line(aes(y = Estimate_adjusted, color = "Adjusted Estimate"), linewidth = 1) +
  geom_point(aes(y = Estimate_adjusted, color = "Adjusted Estimate"), size = 2) +
  # Add unadjusted estimate line
  geom_line(aes(y = Estimate_unadjusted, color = "Naive Estimate"),
            linetype = "dashed", linewidth = 1) +
  # Facet by z_score and effect_estimate
  facet_grid(Z_score ~ Measure,
             labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                                     "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                 Z_score = c("TRUE" = "Selection on Z-score",
                                             "FALSE" = "Selection on log OR/log RR"))) +
  # Define scales for colors and fill
  scale_color_manual(name = " ",
                     values = c("Adjusted Estimate" = "blue", "Naive Estimate" = "red")) +
  scale_fill_manual(name = "Confidence Interval",
                    values = c("Adjusted CI" = "blue", "Unadjusted CI" = "red"),
                    guide = "none") +
  # Add labels and theme adjustments
  labs(x = expression("Selection Weight"~delta), y = "Overall Summary Estimate") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.text = element_text(size = 16))

ggsave("Plots_Paper/App_Uni_REM_O1.png", width = 10, height = 10)
```


# Plot Univariate for seizure freedom

```{r, fig.width = 10, fig.height = 10}
final_uni_df_O2 <- read.csv2("data/data_uni_df_O2.csv", sep = ",")

final_uni_df_O2 <- final_uni_df_O2 %>%
  mutate(across(c(Estimate_adjusted, Estimate_unadjusted,
                   CI_adjusted_lower, CI_adjusted_upper, Estimate_unadjusted,
                  CI_unadjusted_lower, CI_unadjusted_upper), as.numeric))

# plot the different z-scores for unadjusted and adjusted estimates
ggplot(data = final_uni_df_O2, aes(x = as.numeric(Selection))) +
  # Add ribbons for confidence intervals
  geom_ribbon(aes(ymin = CI_adjusted_lower, ymax = CI_adjusted_upper, fill = "Adjusted CI"), alpha = 0.2) +
  geom_ribbon(aes(ymin = CI_unadjusted_lower, ymax = CI_unadjusted_upper, fill = "Unadjusted CI"), alpha = 0.1) +
  # Add adjusted estimate line and point
  geom_line(aes(y = Estimate_adjusted, color = "Adjusted Estimate"), linewidth = 1) +
  geom_point(aes(y = Estimate_adjusted, color = "Adjusted Estimate"), size = 2) +
  # Add unadjusted estimate line
  geom_line(aes(y = Estimate_unadjusted, color = "Naive Estimate"),
            linetype = "dashed", linewidth = 1) +
  # Facet by z_score and effect_estimate
  facet_grid(Z_score ~ Effect_estimate,
             labeller = labeller(Effect_estimate = c("odds_ratio" = "Effect Estimate: Odds Ratio (OR)",
                                                     "relative_risk" = "Effect Estimate: Relative Risk (RR)"),
                                 Z_score = c("TRUE" = "Selection on Z-score",
                                             "FALSE" = "Selection on log OR/log RR"))) +
  # Define scales for colors and fill
  scale_color_manual(name = " ",
                     values = c("Adjusted Estimate" = "blue", "Naive Estimate" = "red")) +
  scale_fill_manual(name = "Confidence Interval",
                    values = c("Adjusted CI" = "blue", "Unadjusted CI" = "red"),
                    guide = "none") +
  # Add labels and theme adjustments
  labs(x = expression("Selection Weight"~delta), y = "Overall Summary Estimate") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.text = element_text(size = 16))

ggsave("Plots_Paper/App_Uni_REM_O2.png", width = 10, height = 10)
```


# Plot Comparison of Correlations
## for 50% Seizure Reduction

```{r, fig.width = 10, fig.height = 10}

plot_biv_df <- read.csv2("Data/data_biv_df_S.csv", sep = ",")

# only plot outcome two
plot_biv_df_O1 <- subset(plot_biv_df, Outcome == "O1")

# bring data into wide format
naive_df_O1 <- plot_biv_df_O1 %>%
 filter(Approach == "Naive estimate") %>%
 dplyr::select(Outcome, Measure, Selection, Correlation,
        Estimate_unadjusted = Estimate,
        CI_unadjusted_lower = CI_Lower,
        CI_unadjusted_upper = CI_Upper)
 
adjusted_df_O1 <- plot_biv_df_O1 %>%
 filter(Approach != "Naive estimate") %>%
 # Create the Z_score column your plot expects (TRUE if zscore, FALSE if effect)
 mutate(Z_score = ifelse(Approach == "Bivariate Selection on zscore", TRUE, FALSE)) %>%
 dplyr::select(Outcome, Measure, Selection, Z_score, Correlation,
        Estimate_adjusted = Estimate, 
        CI_adjusted_lower = CI_Lower, 
        CI_adjusted_upper = CI_Upper)
 
final_biv_df_O1 <- adjusted_df_O1 %>%
 left_join(naive_df_O1, by = c("Selection", "Measure", "Correlation", "Outcome")) 

# plot all correlations together
 
# rename correlations
final_biv_df_O1$Correlation[final_biv_df_O1$Correlation == "studyspecific"] <- "Study-specific"
final_biv_df_O1$Correlation[final_biv_df_O1$Correlation == "estimated"] <- "Global"

# factor correlation such that it is depicted in the correct order in the legend
final_biv_df_O1$Correlation <- factor(
  final_biv_df_O1$Correlation, 
  levels = c("-0.9", "-0.6", "-0.3", "0", "0.3", "0.6", "0.67", "Global", "Study-specific"))

# plot correlation over different colors
ggplot(data = final_biv_df_O1, aes(x = as.numeric(Selection))) +
   # Adjusted estimates: color by Correlation
  geom_line(aes(y = as.numeric(Estimate_adjusted), color = Correlation),
           linewidth = 1, linetype = "solid") +
  geom_point(aes(y = as.numeric(Estimate_adjusted), color = Correlation,
            shape = Correlation), size = 2) +
    # Facets
   facet_grid(Z_score ~ Measure,
              labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                              "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                  Z_score = c("TRUE" = "Selection on Z-score",
                                              "FALSE" = "Selection on log OR/log RR"))) +
     # Manual scales
    scale_color_manual(name = "Correlation",
                      values = c("-0.9" = "lightblue", "-0.6" = "#92C5DE",
                                 "-0.3" = "#4393C3", "0" = "cornflowerblue",
                                 "0.3" = "#2166AC", "0.6" = "skyblue4", "0.67" = "#03045E",
                                 "Study-specific" = "red", "Global" = "forestgreen")) +
    scale_shape_manual(name = "Correlation",
                      values = c("-0.9" = 16, "-0.6" = 17, "-0.3" = 18,
                                 "0" = 19, "0.3" = 20, "0.6" = 0, "0.67" = 5,
                                 "Study-specific" = 21, "Global" = 22)) +
    # Labels and theme
    labs(x = expression("Selection Weight"~delta), y = "Overall Summary Measure") +
    theme_minimal() +
    theme(legend.position = "bottom",
         panel.spacing.x = unit(1, "cm"),
         panel.spacing.y = unit(1, "lines"),
         axis.title.x = element_text(size = 16),
         axis.title.y = element_text(size = 16),
         legend.text = element_text(size = 16),
         legend.title = element_text(size = 16),
         strip.text = element_text(size = 16)) 

ggsave("Plots_Paper/App_Corr_12_mv_REM_O1.png", width = 10, height = 10)

```

## for Seizure Freedom

```{r, fig.width = 10, fig.height = 10}

plot_biv_df <- read.csv2("data/data_biv_df_S.csv", sep = ",")

# only plot outcome two
plot_biv_df <- subset(plot_biv_df, Outcome == "O2")

# bring data into wide format
naive_df <- plot_biv_df %>%
 filter(Approach == "Naive estimate") %>%
 dplyr::select(Outcome, Measure, Selection, Correlation,
        Estimate_unadjusted = Estimate,
        CI_unadjusted_lower = CI_Lower,
        CI_unadjusted_upper = CI_Upper)
 
adjusted_df <- plot_biv_df %>%
 filter(Approach != "Naive estimate") %>%
 # Create the Z_score column your plot expects (TRUE if zscore, FALSE if effect)
 mutate(Z_score = ifelse(Approach == "Bivariate Selection on zscore", TRUE, FALSE)) %>%
 dplyr::select(Outcome, Measure, Selection, Z_score, Correlation,
        Estimate_adjusted = Estimate, 
        CI_adjusted_lower = CI_Lower, 
        CI_adjusted_upper = CI_Upper)
 
final_biv_df <- adjusted_df %>%
 left_join(naive_df, by = c("Selection", "Measure", "Correlation", "Outcome")) 

# plot all correlations together
 
# rename correlations
final_biv_df$Correlation[final_biv_df$Correlation == "studyspecific"] <- "Study-specific"
final_biv_df$Correlation[final_biv_df$Correlation == "estimated"] <- "Global"

# factor correlation such that it is depicted in the correct order in the legend
final_biv_df$Correlation <- factor(
  final_biv_df$Correlation, 
  levels = c("-0.9", "-0.6", "-0.3", "0", "0.3", "0.6", "0.67", "Global", "Study-specific"))


# plot correlation over different colors
ggplot(data = final_biv_df, aes(x = as.numeric(Selection))) +
   # Adjusted estimates: color by Correlation
  geom_line(aes(y = as.numeric(Estimate_adjusted), color = Correlation),
           linewidth = 1, linetype = "solid") +
  geom_point(aes(y = as.numeric(Estimate_adjusted), color = Correlation,
            shape = Correlation), size = 2) +
    # Facets
   facet_grid(Z_score ~ Measure,
              labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                              "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                  Z_score = c("TRUE" = "Selection on Z-score",
                                              "FALSE" = "Selection on log OR/log RR"))) +
     # Manual scales
     scale_color_manual(name = "Correlation",
                      values = c("-0.9" = "lightblue", "-0.6" = "#92C5DE",
                                 "-0.3" = "#4393C3", "0" = "cornflowerblue",
                                 "0.3" = "#2166AC", "0.6" = "skyblue4", "0.67" = "#03045E",
                                 "Study-specific" = "red", "Global" = "forestgreen")) +
     scale_shape_manual(name = "Correlation",
                      values = c("-0.9" = 16, "-0.6" = 17, "-0.3" = 18,
                                 "0" = 19, "0.3" = 20, "0.6" = 0, "0.67" = 5,
                                 "Study-specific" = 21, "Global" = 22)) +
    # Labels and theme
    labs(x = expression("Selection Weight"~delta), y = "Overall Summary Measure") +
    theme_minimal() +
    theme(legend.position = "bottom",
         panel.spacing.x = unit(1, "cm"),
         panel.spacing.y = unit(1, "lines"),
         axis.title.x = element_text(size = 16),
         axis.title.y = element_text(size = 16),
         legend.text = element_text(size = 16),
         legend.title = element_text(size = 16),
         strip.text = element_text(size = 16))

ggsave("Plots_Paper/App_Corr_12_mv_REM_O2.png", width = 10, height = 10)
```

# Plot Univariate and Multivariate for comparison for seizure reduction
## within-study correlation of 0.5

```{r, fig.width = 10, fig.height = 10}

#data set for univariate
uni <- final_uni_df_O1 %>%
  dplyr::select(Z_score, Selection, Measure,
                Estimate_adjusted_uni = Estimate_adjusted,
                Estimate_unadjusted_uni = Estimate_unadjusted,
                CI_adjusted_low_uni = CI_adjusted_lower,
                CI_adjusted_up_uni = CI_adjusted_upper)

uni$Selection <- as.numeric(uni$Selection)
final_biv_df_O1$Selection <- as.numeric(final_biv_df_O1$Selection)

# select correlation
final_biv_df_O1 <- subset(final_biv_df_O1, Correlation == -0.3)

# merge with bivariate data
plotdf <- final_biv_df_O1 %>%
  dplyr::select(Z_score, Selection, Measure,
                Estimate_adjusted, Estimate_unadjusted,
                CI_adjusted_lower, CI_adjusted_upper) %>%
  left_join(uni, by = c("Measure", "Z_score","Selection"))

# make sure estimates are numerical
plotdf <- plotdf %>%
  mutate(across(c(Estimate_adjusted, Estimate_unadjusted,
                   CI_adjusted_lower, CI_adjusted_upper,
                  Estimate_adjusted_uni, Estimate_unadjusted_uni,
                  CI_adjusted_low_uni, CI_adjusted_up_uni), as.numeric))


# Create the ggplot
ggplot(data = plotdf, aes(x = as.numeric(Selection))) +
  # Add ribbons for confidence intervals
  geom_ribbon(aes(ymin = as.numeric(CI_adjusted_low_uni), ymax = as.numeric(CI_adjusted_up_uni), fill = "Adjusted CI Univariate"), alpha = 0.2) +
  geom_ribbon(aes(ymin = CI_adjusted_lower, ymax = CI_adjusted_upper, fill = "Adjusted CI Bivariate"), alpha = 0.1) +
  # Add adjusted estimate line and point
  geom_line(aes(y = as.numeric(Estimate_adjusted), color = "Adjusted - Bivariate"), linewidth = 1) +
  geom_line(aes(y = as.numeric(Estimate_adjusted_uni), color = "Adjusted - Univariate"), linewidth = 1) +
  geom_point(aes(y = as.numeric(Estimate_adjusted), color = "Adjusted - Bivariate"), size = 2) +
  geom_point(aes(y = as.numeric(Estimate_adjusted_uni), color = "Adjusted - Univariate"), size = 2) +
  # Add unadjusted estimate line
  geom_line(aes(y = as.numeric(Estimate_unadjusted), color = "Naive - Bivariate"), linetype = "dashed", linewidth = 1) +
  geom_line(aes(y = as.numeric(Estimate_unadjusted_uni), color = "Naive - Univariate"), linetype = "dashed", linewidth = 1) +
  # Facet by z_score and effect_estimate
  facet_grid(Z_score ~ Measure,
             labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                             "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                 Z_score = c("TRUE" = "Selection on Z-score",
                                             "FALSE" = "Selection on log OR/log RR"))) +
  # Define scales for colors and fill
  scale_color_manual(name = " ",
                     values = c("Adjusted - Univariate" = "blue",
                                "Adjusted - Bivariate" = "#009E73",
                                "Naive - Bivariate" = "#009E73",
                                "Naive - Univariate" = "blue")) +
  scale_fill_manual(name = "Confidence Interval",
                    values = c("Adjusted CI Univariate" = "blue",
                               "Adjusted CI Bivariate" = "#009E73"),
                    guide = "none") +
  # Add labels and theme adjustments
  labs(x = expression("Selection Weight"~delta), y = "Overall Summary Measure") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.spacing.x = unit(1, "cm"),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.text = element_text(size = 16))

ggsave("Plots_Paper/Uni_Multi_Comp_12_REM_05_01.png", width = 10, height = 10)
```


# Plot Univariate and Multivariate for comparison for seizure freedom
## within-study correlation of 0.5

```{r, fig.width = 10, fig.height = 10}

#data set for univariate
uni <- final_uni_df_O2 %>%
  dplyr::select(Z_score, Selection, Measure,
                Estimate_adjusted_uni = Estimate_adjusted,
                Estimate_unadjusted_uni = Estimate_unadjusted,
                CI_adjusted_low_uni = CI_adjusted_lower,
                CI_adjusted_up_uni = CI_adjusted_upper)

uni$Selection <- as.numeric(uni$Selection)
final_biv_df$Selection <- as.numeric(final_biv_df$Selection)

# select correlation
final_biv_df1 <- subset(final_biv_df, Correlation == -0.3)

# merge with bivariate data
plotdf <- final_biv_df1 %>%
  dplyr::select(Z_score, Selection, Measure,
                Estimate_adjusted, Estimate_unadjusted,
                CI_adjusted_lower, CI_adjusted_upper) %>%
  left_join(uni, by = c("Measure", "Z_score","Selection"))

# make sure estimates are numerical
plotdf <- plotdf %>%
  mutate(across(c(Estimate_adjusted, Estimate_unadjusted,
                   CI_adjusted_lower, CI_adjusted_upper,
                  Estimate_adjusted_uni, Estimate_unadjusted_uni,
                  CI_adjusted_low_uni, CI_adjusted_up_uni), as.numeric))


# Create the ggplot
ggplot(data = plotdf, aes(x = as.numeric(Selection))) +
  # Add ribbons for confidence intervals
  geom_ribbon(aes(ymin = as.numeric(CI_adjusted_low_uni), ymax = as.numeric(CI_adjusted_up_uni), fill = "Adjusted CI Univariate"), alpha = 0.2) +
  geom_ribbon(aes(ymin = CI_adjusted_lower, ymax = CI_adjusted_upper, fill = "Adjusted CI Bivariate"), alpha = 0.1) +
  # Add adjusted estimate line and point
  geom_line(aes(y = as.numeric(Estimate_adjusted), color = "Adjusted - Bivariate"), linewidth = 1) +
  geom_line(aes(y = as.numeric(Estimate_adjusted_uni), color = "Adjusted - Univariate"), linewidth = 1) +
  geom_point(aes(y = as.numeric(Estimate_adjusted), color = "Adjusted - Bivariate"), size = 2) +
  geom_point(aes(y = as.numeric(Estimate_adjusted_uni), color = "Adjusted - Univariate"), size = 2) +
  # Add unadjusted estimate line
  geom_line(aes(y = as.numeric(Estimate_unadjusted), color = "Naive - Bivariate"), linetype = "dashed", linewidth = 1) +
  geom_line(aes(y = as.numeric(Estimate_unadjusted_uni), color = "Naive - Univariate"), linetype = "dashed", linewidth = 1) +
  # Facet by z_score and effect_estimate
  facet_grid(Z_score ~ Measure,
             labeller = labeller(Measure = c("log OR" = "Effect Estimate: Odds Ratio (OR)",
                                             "log RR" = "Effect Estimate: Relative Risk (RR)"),
                                 Z_score = c("TRUE" = "Selection on Z-score",
                                             "FALSE" = "Selection on log OR/log RR"))) +
  # Define scales for colors and fill
  scale_color_manual(name = " ",
                     values = c("Adjusted - Univariate" = "blue",
                                "Adjusted - Bivariate" = "#009E73",
                                "Naive - Bivariate" = "#009E73",
                                "Naive - Univariate" = "blue")) +
  scale_fill_manual(name = "Confidence Interval",
                    values = c("Adjusted CI Univariate" = "blue",
                               "Adjusted CI Bivariate" = "#009E73"),
                    guide = "none") +
  # Add labels and theme adjustments
  labs(x = expression("Selection Weight"~delta), y = "Overall Summary Measure") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.spacing.x = unit(1, "cm"),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.text = element_text(size = 16))

ggsave("Plots_Paper/Uni_Multi_Comp_12_REM_05.png", width = 10, height = 10)
```

## create forest plot

```{r}
# read data in from Table_2.rds
data <- readRDS("data/Table_2.rds")

# transform data to plot them as forest plot
dat <- data %>%
  # Standardize Approach names 
  mutate(
    Approach = case_when(
      Approach == "Selection on effect" ~ "Selection on effect estimate",
      Approach == "Selection on zscore" ~ "Selection on z-score",
      Approach == "Bivariate Selection on effect" ~ "Selection on effect estimate",
      Approach == "Bivariate Selection on zscore" ~ "Selection on z-score",
      TRUE ~ Approach
    ),
    #  Re-format the Model column
    Model = if_else(Correlation == "Univariate", "Univariate", paste0("Bivariate (", Correlation, ")")),
    # Clean up the Measure column
    Effect = str_remove(Measure, "log ")
  ) %>%
  # Pivot the two outcomes into a long format
  pivot_longer(
    cols = starts_with("Outcome"),
    names_to = c("Outcome", ".value"),
    names_pattern = "Outcome (\\d+)_(.*)"
  ) %>%
  #  Rename outcome numbers to your descriptive labels
  mutate(
    Outcome = if_else(Outcome == "1", "50% Seizure Reduction", "Seizure Freedom")
  ) %>%
  mutate(est = str_remove(Est_SE, " \\(.*\\)"
                          )) %>%
  #  Separate the confidence intervals into low (lcl) and high (ucl) bounds
  separate_wider_delim(
    cols = CI_95, 
    delim = " to ", 
    names = c("lcl", "ucl")
  ) %>%
  # Clean up data types 
  mutate(
    lcl = as.numeric(lcl),
    ucl = as.numeric(ucl),
    est = as.numeric(est)
  ) %>%
  #select/reorder the final columns
  select(Model, Effect, Approach, Outcome, est, lcl, ucl)
```


```{r}
# Ordering
dat <- dat %>%
  mutate(
    Model = factor(
      Model,
      levels = c("Univariate",
                 "Bivariate (r = 0)",
                 "Bivariate (r = 0.7)")),
    Approach = factor(
      Approach,
      levels = c("Naive estimate",
                 "Selection on effect estimate",
                 "Selection on z-score"))) %>%
  arrange(Model, Approach)

# create the label for ploting
dat$Label <- factor(
  dat$Approach,
  levels = rev(c("Naive estimate",
                 "Selection on effect estimate",
                 "Selection on z-score")))

dat$Label <- factor(dat$Label,
                   levels = rev(unique(dat$Label)))
```

```{r, fig.width=10, fig.height=6}

# have enough space between imputation models, otherwise they are plotted on
# top of each other
pd <- position_dodge(width = 0.6, 
                     reverse = TRUE)

ggplot(dat,
       aes(x = est, y = Label, xmin = lcl, xmax = ucl, colour = Model)) +
  geom_vline(xintercept = 0, linetype = 2, colour = "grey40") +
  geom_errorbarh(width = 0.15, linewidth = 0.7, position = pd) +
  geom_point(size = 3, position = pd) +
  facet_grid(Effect ~ Outcome, 
             scales = "free_y", space = "free_y") +
  labs(x = "Log (OR)/ Log (RR)",
       y = NULL,
       colour = "Imputation model") +
  theme_bw(base_size = 16) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        strip.background = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        strip.text = element_text(face = "bold"),
        axis.text.y = element_text(size = 16, colour = "black"))


ggsave("Plots_Paper/Forestplot.png", width = 10, height = 6)
```

